### 2014-12-21 msr.tex
initial commit msr2015

\pdfpagewidth=8.5in 
\pdfpageheight=11in

\documentclass{sig-alternate}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage{microtype}

\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{color}

\usepackage{flushend}

\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

\begin{document}

\conferenceinfo{MSR}{'15, May 16 – 17, 2015, Florence, Italy}
\CopyrightYear{2015}
\crdata{978-1-4503-2863-0/14/05}

\title{The Bug Catalog of the Maven Ecosystem}

\numberofauthors{2}

\author{
\alignauthor Vassilios Karakoidas\\
       \affaddr{Athens University of Economics and Business}\\
       \affaddr{Department of Management Science and Technology}\\
       \email{bkarak@aueb.gr}
\alignauthor Georgios Gousios\\
       \affaddr{--}\\
       \affaddr{--}\\
       \email{aa@bb.com}       
}

\maketitle
\begin{abstract}

\end{abstract}

\category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical methods]
\category{D.2.7}{Software Engineering}{Distribution, Maintenance, and Enhancement}[Version control]

\terms{Static Analysis, Software Ecosystems.}

\keywords{Maven Repository, JDepend, Software Bugs.}

\section{Introduction}
\label{sec:intro}

\section{Dataset Contents}
\label{sec:data}

\section{Harnessing Our Dataset}
\label{sec:exploit}

\section{Limitations}
\label{sec:limit}

\section{Related Work}
\label{sec:rel}

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, this dataset
also includes a database with all the
connections between the aforementioned elements.
Our work differs from this research because it
reports all bugs coming from the output of a
static analysis tool, for each {\sc jar}
contained in the Maven repository.

\cite{MKLGS14}

\section{Conclusions}
\label{sec:conc}

\bibliographystyle{abbrv}
\bibliography{msr}

\end{document}

### 2015-01-10 msr.tex
adding stuff

@@
 
-\title{The Bug Catalog of the Maven Ecosystem}
+\title{The Three Corridors}
 
-\numberofauthors{2}
+\numberofauthors{5}
+
+\def\aueb{\textsuperscript{*}}
+\def\tud{\textsuperscript{\dag}}
 
 \author{
-\alignauthor Vassilios Karakoidas\\
-       \affaddr{Athens University of Economics and Business}\\
-       \affaddr{Department of Management Science and Technology}\\
-       \email{bkarak@aueb.gr}
-\alignauthor Georgios Gousios\\
-       \affaddr{--}\\
-       \affaddr{--}\\
-       \email{aa@bb.com}       
+  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\tud \and Diomidis Spinellis\aueb \\
+  \begin{tabular}{ccc}
+  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\tud Software Engineering Research Group}\\
+    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\tud Delft University of Technology}\\
+   \affaddr{Athens, Greece} & & \affaddr{Delft, the Netherlands}\\
+   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{g.gousios@tudelft.nl} \\
+  \end{tabular}
 }
@@
 
+\begin{table}
+\centering
+\caption{The selected Maven projects' size metrics}
+\label{tbl:oss-size-metrics}
+\begin{tabular}{l r}
+ \hline
+\textbf{Metric} & \textbf{Value}\\ 
+\hline
+Project Count & 12,959\\
+File Count & 604,821\\
+Module Count & 72,302\\
+Lines of Code & 110,156,703\\
+Source Lines of Code & 61,246,807\\
+Comment Lines of Code & 36,696,217\\
+Number of Classes & 499,588\\
+Number of Interfaces & 89,145\\
+Number of Enumerations & 12,732\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Selected Metrics}
+\label{tbl:selected-metrics}
+\begin{tabular}{l l}
+ \hline
+\multicolumn{2}{l}{\textit{\textbf{Class \& Method Design}}}\\
+\hline
+Depth Of Inheritance Tree & \textit{ckjm}\\
+Coupling Between Objects & \textit{ckjm}\\
+Weighted Methods Per Class & \textit{ckjm}\\
+Response For Class & \textit{ckjm}\\
+Lack Of Cohesion In Methods & \textit{ckjm}\\
+Number Of Children & \textit{ckjm}\\
+Attribute Hiding Factor & \textit{clmt}\\
+Coupling Between Methods & \textit{ckjm}\\ 
+Average Method Complexity & \textit{ckjm}\\
+Cohesion Among Methods of Class & \textit{ckjm}\\
+Data Access Metric & \textit{ckjm}\\ 
+Inheritance Coupling & \textit{ckjm}\\
+Lack Of Cohesion In Methods3 & \textit{ckjm}\\ 
+McCabe Cyclomatic Complexity & \textit{ckjm}\\
+Measure Of Aggregation & \textit{ckjm}\\
+Measure Of Functional Abstraction & \textit{ckjm}\\
+Method Hiding Factor & \textit{clmt}\\
+\hline
+\multicolumn{2}{l}{\textit{\textbf{Package Design}}}\\
+\hline
+Afferent Couplings & \textit{jdep}\\
+Efferent Couplings & \textit{jdep}\\
+Instability & \textit{jdep}\\
+Abstractness & \textit{jdep}\\
+Distance Main Sequence & \textit{jdep}\\
+\hline
+\multicolumn{2}{l}{\textit{\textbf{Program Size Metrics}}}\\
+\hline
+Comments Lines Of Code & \textit{clmt}\\
+Lines Of Code & \textit{clmt}\\
+Native Methods Per Code Unit & \textit{clmt}\\
+Native Methods Per Project & \textit{clmt}\\
+Source Lines Of Code & \textit{clmt}\\ 
+Function Oriented Code & \textit{clmt}\\
+\hline
+\end{tabular}
+\end{table}
+
 \section{Harnessing Our Dataset}
@@
 \label{sec:limit}
+
+\section{On the Use of Domain Specific Languages}
+\label{sec:dsl}
+
+The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications.
+The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition SDK.
+The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.
+
+In the literature, it is referred that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}.
+This thesis focuses on practical research aspects as well as with the theoretical ones; thus the first problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects.
+In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.
+
+The methodology was the following; A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
+\textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used.
+If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}.
+Consequently, if a project has {\sc dsl} count four (4), then it means that four (4) different application libraries were detected during the source code scan.
+Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
+Note that all these libraries are included as part of the Java {\sc sdk}.
+
+\begin{table}
+\centering
+\caption{List of selected DSL application libraries}
+\label{tbl:dsl-list}
+\begin{tabular}{l l}
+ \hline
+\textbf{DSL} & \textbf{Java Package}\\
+\hline
+Regular Expressions & \verb|java.util.regex|\\
+XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
+SQL & \verb|java.sql| and \verb|javax.sql|\\
+XPath & \verb|java.xml.xpath|\\
+XSLT & \verb|javax.xml.transform|\\
+RTF & \verb|javax.swing.text.rtf|\\
+HTML & \verb|javax.swing.text.html|\\
+\hline
+\end{tabular}
+\end{table}
+
+The initial goal of this experiment was simply to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account.
+Build files or other resources that may contain {\sc dsl}s were not included.
+
+One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.
 

### 2015-01-10 msr.tex
bulk add

@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=0.65]{dsl-usage}
+\caption{DSL language usage in Java projects}
+\label{fig:dsl-usage}
+\end{figure}
+
+\begin{table}
+\centering
+\caption{Popular DSL Usage Combinations}
+\label{tbl:dsl-top-usage}
+\begin{tabular}{l r}
+ \hline
+\textbf{DSLs} & \textbf{Count}\\
+\hline
+XML & 1,561\\
+Regex & 909\\
+SQL & 493\\
+XML, XSLT & 475\\
+Regex, XML, XSLT & 158\\
+Regex, XML & 303\\
+SQL, XML & 162\\
+Regex, SQL & 116\\
+Regex, SQL, XML, XSLT & 80\\
+Regex, SQL, XML & 71\\
+SQL, XML, XSLT & 54\\
+XML, XPath & 50\\
+XML, XPath, XSLT & 39\\
+Regex, XML, XPath, XSLT & 38\\
+HTML & 23\\
+Regex, XML, XPath & 20\\
+Regex, SQL, XML, XPath, XSLT & 18\\
+SQL, XML, XPath, XSLT & 11\\
+HTML, Regex, XML & 10\\
+HTML, XML & 10\\
+\hline
+\end{tabular}
+\end{table}
+
 \section{Related Work}

### 2015-01-10 msr.tex
adding text

@@
 
+Software metrics provide a means to extract useful and measurable information about the structure of a software system.
+Since software artefacts consist of digital data, many of their aspects are easily measured.
+This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early.
+Over the years, a wealth of different metrics has appeared in the literature \cite{GUSC07,BBM96,LOKI94,HK81,BDM97} and some of them, like Chidamber and Kemerer \cite{CHKE94} have found their way in software development practice and tools.
+
+Today a software engineer or developer has a very large list of metrics at his disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system.
+This has led researchers to try to discover which set of metrics is most appropriate for each environment \cite{XSZC00,PUVA03,MAHA99,BRCA94}.
+There also exist metrics that can be used to evaluate other aspects of a system, such as the process that was used to develop it.
+
 \section{Dataset Contents}
 \label{sec:data}
+
+\begin{itemize}
+  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
+It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.
+
+  \item \textbf{JDepend} \textit{(jdep)}
+
+  \item \textbf{CLMT} \textit{(clmt)}
+\end{itemize}
 
@@
 
-\section{Harnessing Our Dataset}
-\label{sec:exploit}
-
-\section{Limitations}
-\label{sec:limit}
-
 \section{On the Use of Domain Specific Languages}
@@
 The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications.
-The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition SDK.
+The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc dsk}.
 The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.
@@
 
+\section{Limitations}
+\label{sec:limit}
+
 \section{Related Work}
@@
 
-The Maven ecosystem has been previously analyzed by
-Raemaekers et al.~\cite{RDV13}
-to produce the {\it Maven dependency dataset}.
-Apart from basic information like individual methods, classes,
-packages and lines of code for every {\sc jar}, this dataset
-also includes a database with all the
-connections between the aforementioned elements.
-Our work differs from this research because it
-reports all bugs coming from the output of a
-static analysis tool, for each {\sc jar}
-contained in the Maven repository.
+The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}.
+Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements.
+Our work differs from this research because it reports all bugs coming from the output of a static analysis tool, for each {\sc jar} contained in the Maven repository.
 
-\cite{MKLGS14}
+\cite{MKLGS14} \cite{KARA14}
 

### 2015-01-10 msr.tex
update msr.tex

@@
 
-\keywords{Maven Repository, JDepend, Software Bugs.}
+\keywords{Maven Repository, JDepend, Software Metrics, Chidamber and Kemerer.}
 
@@
 \label{sec:data}
+
+ Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation\footnote{\url{http://www.apache.org/}}.
+To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}.
+The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis.
+These languages include Java, Clojure, Groovy, and Scala.
+
+Initially, a snapshot (January 2012) of the Maven repository was downloaded locally.
+The repository contains various projects and their releases.
+A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}.
+The Maven repository contains several versions of each project.
+
+All versions were filtered out and only the latest was kept.
+For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code.
+Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus.
+It included 12,959 projects, with more than 110 million lines of code.
 

### 2015-01-24 msr.tex
added msr.tex
added database-schema
added database structure section

@@
 \centering
-\caption{Selected Metrics}
+\caption{Available Metrics}
 \label{tbl:selected-metrics}
@@
 Cohesion Among Methods of Class & \textit{ckjm}\\
-Data Access Metric & \textit{ckjm}\\ 
+Data Access Metric & \textit{ckjm, clmt}\\
 Inheritance Coupling & \textit{ckjm}\\
 Lack Of Cohesion In Methods3 & \textit{ckjm}\\
-McCabe Cyclomatic Complexity & \textit{ckjm}\\
+McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
 Measure Of Aggregation & \textit{ckjm}\\
@@
 \hline
-Afferent Couplings & \textit{jdep}\\
-Efferent Couplings & \textit{jdep}\\
+Afferent Couplings & \textit{jdep, ckjm}\\
+Efferent Couplings & \textit{jdep, ckjm}\\
 Instability & \textit{jdep}\\
@@
 \hline
+Module Count & \textit{clmt}\\
 Comments Lines Of Code & \textit{clmt}\\
-Lines Of Code & \textit{clmt}\\
+Lines Of Code & \textit{clmt, ckjm}\\
 Native Methods Per Code Unit & \textit{clmt}\\
@@
 Function Oriented Code & \textit{clmt}\\
+DSL Usage Count & \textit{clmt}\\
+File Count & \textit{clmt}\\
 \hline
@@
 \end{table}
+
+\section{Database Structure}
+\label{sec:db}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.7]{database-schema}
+\end{figure*}
 

### 2015-01-24 msr.tex
updated msr.tex
added .gitignore

--- 2015-01-10 msr.tex
@@
 \centering
-\caption{Selected Metrics}
+\caption{Key Metrics}
 \label{tbl:selected-metrics}
@@
  \hline
-\multicolumn{2}{l}{\textit{\textbf{Class \& Method Design}}}\\
+\multicolumn{2}{l}{\textit{\textbf{Class Design}}}\\
 \hline
@@
 Cohesion Among Methods of Class & \textit{ckjm}\\
-Data Access Metric & \textit{ckjm}\\ 
+Data Access Metric & \textit{ckjm, clmt}\\
 Inheritance Coupling & \textit{ckjm}\\
 Lack Of Cohesion In Methods3 & \textit{ckjm}\\
-McCabe Cyclomatic Complexity & \textit{ckjm}\\
 Measure Of Aggregation & \textit{ckjm}\\
 Measure Of Functional Abstraction & \textit{ckjm}\\
+Number of Attributes & \textit{clmt}\\
 Method Hiding Factor & \textit{clmt}\\
+\hline
+\multicolumn{2}{l}{\textit{\textbf{Method Design}}}\\
+\hline
+Number of Method Parameters & \textit{clmt}\\
+Number of Methods & \textit{clmt, ckjm}\\
+McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
 \hline
@@
 \hline
-Afferent Couplings & \textit{jdep}\\
-Efferent Couplings & \textit{jdep}\\
+Number of Concrete Classes & \textit{jdep}\\
+Afferent Couplings & \textit{jdep, ckjm}\\
+Efferent Couplings & \textit{jdep, ckjm}\\
 Instability & \textit{jdep}\\
@@
 \hline
+Number of Classes & \textit{clmt, ckjm, jdep}\\
+Number of Enumerations & \textit{clmt, ckjm}\\
+Number of Interfaces & \textit{clmt, ckjm}\\
+Module Count & \textit{clmt, ckjm}\\
 Comments Lines Of Code & \textit{clmt}\\
-Lines Of Code & \textit{clmt}\\
-Native Methods Per Code Unit & \textit{clmt}\\
-Native Methods Per Project & \textit{clmt}\\
+Lines Of Code & \textit{clmt, ckjm}\\
 Source Lines Of Code & \textit{clmt}\\
 Function Oriented Code & \textit{clmt}\\
+DSL Usage Count & \textit{clmt}\\
+File Count & \textit{clmt}\\
 \hline
@@
 \end{table}
+
+\section{Database Structure}
+\label{sec:db}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.7]{database-schema}
+\caption{The database schema}
+\label{fig:database-schema}
+\end{figure*}
 

### 2015-01-24 msr.tex
added bibliographic entries
working on introduction

@@
 This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early.
-Over the years, a wealth of different metrics has appeared in the literature \cite{GUSC07,BBM96,LOKI94,HK81,BDM97} and some of them, like Chidamber and Kemerer \cite{CHKE94} have found their way in software development practice and tools.
-
-Today a software engineer or developer has a very large list of metrics at his disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system.
-This has led researchers to try to discover which set of metrics is most appropriate for each environment \cite{XSZC00,PUVA03,MAHA99,BRCA94}.
-There also exist metrics that can be used to evaluate other aspects of a system, such as the process that was used to develop it.
+Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al.
+\cite{LOKI94} that have found their way in software development practice and tools.
+Today a software engineer or developer has a very large list of metrics at her disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system.
 

### 2015-01-25 msr.tex
added title

@@
 
-\title{The Three Corridors}
+\title{Generating the Blueprints of the Maven Repository}
 
@@
 
-\begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
-It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.
-
-  \item \textbf{JDepend} \textit{(jdep)}
-
-  \item \textbf{CLMT} \textit{(clmt)}
-\end{itemize}
-
 \begin{table}
@@
 \end{table}
+
+\section{The Toolset}
+
+Three tools were selected.
+
+\begin{itemize}
+  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
+It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.
+The version of the tool that we used for this experinment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.
+
+  \item \textbf{JDepend} \textit{(jdep)}\footnote{\url{http://clarkware.com/software/JDepend.html}} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
+
+  \item \textbf{CLMT} \textit{(clmt)} stands for cross-language metric tool and analyses Java source code in order to calculate a series of metrics.
+\end{itemize}
+
+Table~\ref{tbl:selected-metrics} presents the key metrics that exist in the dataset. Note that each tool
 

### 2015-01-25 msr.tex
Add ckjm citation

@@
 \begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
 It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.

### 2015-01-25 msr.tex
Fix my affiliation

@@
 \def\aueb{\textsuperscript{*}}
-\def\tud{\textsuperscript{\dag}}
+\def\run{\textsuperscript{\dag}}
 
 \author{
-  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\tud \and Diomidis Spinellis\aueb \\
+  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb \\
   \begin{tabular}{ccc}
-  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\tud Software Engineering Research Group}\\
-    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\tud Delft University of Technology}\\
-   \affaddr{Athens, Greece} & & \affaddr{Delft, the Netherlands}\\
-   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{g.gousios@tudelft.nl} \\
+  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\run Department of Digital Security}\\
+    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\run Radboud University Nijmegen}\\
+   \affaddr{Athens, Greece} & & \affaddr{Nijmegen, the Netherlands}\\
+   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{georgios@cs.ru.nl} \\
   \end{tabular}

### 2015-02-22 msr.tex
title changed
minor edit

--- 2015-01-25 msr.tex
@@
 
-\title{Generating the Blueprints of the Maven Repository}
+\title{Generating the Blueprints of Java Ecosystem}
 
@@
 Software metrics provide a means to extract useful and measurable information about the structure of a software system.
-Since software artefacts consist of digital data, many of their aspects are easily measured.
+Since software artifacts consist of digital data, many of their aspects are easily measured.
 This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early.
@@
 It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.
-The version of the tool that we used for this experinment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.
+The version of the tool that we used for this experiment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.
 
@@
 The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications.
-The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc dsk}.
+The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.
 The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.

### 2015-02-22 msr.tex
converting footnote urls to bib entries; working on the text a little

@@
 \category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical methods]
-\category{D.2.7}{Software Engineering}{Distribution, Maintenance, and Enhancement}[Version control]
 
@@
 
-\keywords{Maven Repository, JDepend, Software Metrics, Chidamber and Kemerer.}
+\keywords{JDepend, Software Metrics, Chidamber and Kemerer.}
 
@@
 Since software artifacts consist of digital data, many of their aspects are easily measured.
-This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early.
+This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early.
 Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al.
 \cite{LOKI94} that have found their way in software development practice and tools.
-Today a software engineer or developer has a very large list of metrics at her disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system.
 
@@
 \begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
-It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.
-The version of the tool that we used for this experiment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.
+  \item \textbf{CKJM-ext} \textit{(ckjm)} \cite{CKJMDDS} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
+It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
+The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.
 
@@
 
-\section{On the Use of Domain Specific Languages}
+\section{Experimenting with the Dataset}
 \label{sec:dsl}

### 2015-02-22 msr.tex

@@
 \begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)} \cite{CKJMDDS} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
+
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
 It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.

### 2015-02-22 msr.tex
one footnote url left

@@
 
-  \item \textbf{JDepend} \textit{(jdep)}\footnote{\url{http://clarkware.com/software/JDepend.html}} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
+  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
 

### 2015-02-22 msr.tex
putting stuff on the paper

@@
 
- Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation\footnote{\url{http://www.apache.org/}}.
+ Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}.
 To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}.
@@
 
-Table~\ref{tbl:selected-metrics} presents the key metrics that exist in the dataset. Note that each tool
+Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
+Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on
 
@@
 \label{sec:db}
+
+Figure~\ref{fig:database-schema} illustrates the database
 
@@
 
-\cite{MKLGS14} \cite{KARA14}
+In publication \cite{MKLGS14}, a
 
@@
 \label{sec:conc}
+
+\section{Availability}
+
+The dataset and the source code of this publication, along with some utility scripts are available at \url{https://github.com/bkarak/data_msr2015}.
 

### 2015-02-22 msr.tex
almost there with The Three Tools section

@@
 
-\section{The Toolset}
+\section{The Three Tools}
 
@@
 \begin{itemize}
-
   \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
@@
 
-  \item \textbf{CLMT} \textit{(clmt)} stands for cross-language metric tool and analyses Java source code in order to calculate a series of metrics.
+  \item \textbf{CLMT} \textit{(clmt)} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
 \end{itemize}
@@
 Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
-Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on
+Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
+Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
+Both calculation are stored and provided by the dataset.
 

### 2015-02-22 msr.tex
a little work on related work

@@
 
-  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
+  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
 
@@
 
-Figure~\ref{fig:database-schema} illustrates the database
+Figure~\ref{fig:database-schema} illustrates the database schema. The data are stored in a straightforward manner.
 
@@
 Build files or other resources that may contain {\sc dsl}s were not included.
-
 One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.65]{dsl-usage}
-\caption{DSL language usage in Java projects}
-\label{fig:dsl-usage}
-\end{figure}
 
@@
 Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements.
-Our work differs from this research because it reports all bugs coming from the output of a static analysis tool, for each {\sc jar} contained in the Maven repository.
-
-In publication \cite{MKLGS14}, a
+In publication \cite{MKLGS14}, Mitropoulos et al.
+also experimented in a similar way, by running the findbugs~\cite{HP04} security and bugs audit tool on a large part of the maven repository.
+Our work differs from these these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.
 

### 2015-02-22 msr.tex
working on the text

@@
 
-Figure~\ref{fig:database-schema} illustrates the database schema. The data are stored in a straightforward manner.
+Figure~\ref{fig:database-schema} illustrates the database schema.
+The data are stored in a straightforward manner.
+The database schema consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
+The central table is \textit{measurement}, which holds the actual measurement values.
+The other tables are used as normalisation tables.
+
+Metrics are divided in six categories that defined its scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}.
+These values are stored in \textit{category} table.
+
+The descriptive names for each metric are stored in the \textit{measurement\_type} table.
+There are 65 metrics available in the dataset.
+The names are composed by the actual metric name and the tool that was used to calculate them e.g.
+\textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the clmt tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the ckjm tool.
+
+Filenames, method, class and package names along with other identifiers are stored in the \textit{identifiers} table.
+Note that each measurement has a related filename and a related identifier that points to the software element that is related e.g.
+the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related with the identifier \textit{com.scalagent.jmx}.
+
+Finally the table \textit{project} contains the related project identifiers, extracted from the maven repository.
 

### 2015-02-22 msr.tex
reorganised tools

@@
 This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early.
-Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer \cite{CHKE94} and those presented by Lorenz et al.
-\cite{LOKI94} that have found their way in software development practice and tools.
+Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} that have found their way in software development practice and tools.
 
@@
 
+Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
+Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
+Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
+Both calculation are stored and provided by the dataset.
 Three tools were selected.
@@
 \end{itemize}
-
-Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
-Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
-Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
-Both calculation are stored and provided by the dataset.
 

### 2015-02-22 msr.tex
updated msr.tex
added valid jars

@@
 It included 12,959 projects, with more than 110 million lines of code.
+Overall the dataset contains almost 33 million unique measurements.
 
@@
 \hline
-Project Count & 12,959\\
+Project Count & 11,365\\
 File Count & 604,821\\
@@
 Number of Enumerations & 12,732\\
+Measurement Count & 32,844,836\\
 \hline
@@
 Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
-Both calculation are stored and provided by the dataset.
-Three tools were selected.
+Both calculation are stored and provided by the dataset.Three tools were selected.
 

### 2015-02-22 msr.tex
changed aff

@@
 \def\aueb{\textsuperscript{*}}
+\def\columbia{\textsuperscript{\ddag}}
 \def\run{\textsuperscript{\dag}}
@@
   Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb \\
-  \begin{tabular}{ccc}
-  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\run Department of Digital Security}\\
-    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\run Radboud University Nijmegen}\\
-   \affaddr{Athens, Greece} & & \affaddr{Nijmegen, the Netherlands}\\
-   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{georgios@cs.ru.nl} \\
+  \begin{tabular}{cccccc}
+   \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\run Department of Digital Security}
+  & & \affaddr{\columbia Computer Science Department} \\
+    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\run Radboud University Nijmegen}
+  & & \affaddr{Columbia University} \\
+   \affaddr{Athens, Greece} & & \affaddr{Nijmegen, the Netherlands} && \affaddr{New York, United States} \\
+   \email{\{bkarak,louridas,dds\}@aueb.gr} & & \email{georgios@cs.ru.nl} & & \email{dimitro@cs.columbia.edu} \\
   \end{tabular}

### 2015-02-22 msr.tex
fixed authors (almost)

--- 2015-02-22 msr.tex
@@
 \author{
-  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\aueb \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb \\
-  \begin{tabular}{ccc}
-  \affaddr{\aueb Department of Management Science and Technology} & & \affaddr{\run Department of Digital Security}\\
-    \affaddr{\aueb Athens University of Economics and Business} & & \affaddr{\run Radboud University Nijmegen}\\
-   \affaddr{Athens, Greece} & & \affaddr{Nijmegen, the Netherlands}\\
-   \email{\{bkarak,dimitro,louridas,dds\}@aueb.gr}& & \email{georgios@cs.ru.nl} \\
+  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
+  \begin{tabular}{p{7cm} p{5cm} p{5cm}}
+   \affaddr{\aueb Department of Management Science and Technology} & \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
+   \affaddr{Athens University of Economics and Business} & \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
+   \affaddr{Athens, Greece} & \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
+   \email{\{bkarak,louridas,dds\}@aueb.gr} & \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
   \end{tabular}

### 2015-02-22 msr.tex
almost there with the authors

@@
   Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
-  \begin{tabular}{p{7cm} p{5cm} p{5cm}}
-   \affaddr{\aueb Department of Management Science and Technology} & \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
+  \begin{tabular}{p{6cm} p{5cm} p{5cm}}
+   \affaddr{\aueb Dept of Management Science and Technology} & \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
    \affaddr{Athens University of Economics and Business} & \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\

### 2015-02-22 msr.tex
updated authors

@@
   Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
-  \begin{tabular}{p{6cm} p{5cm} p{5cm}}
-   \affaddr{\aueb Dept of Management Science and Technology} & \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
-   \affaddr{Athens University of Economics and Business} & \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
-   \affaddr{Athens, Greece} & \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
-   \email{\{bkarak,louridas,dds\}@aueb.gr} & \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
+  \begin{tabular}{cc}
+   \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
+   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
+   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
+   \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
+  \end{tabular}
+  \centering
+  \begin{tabular}{c}
+   \affaddr{\aueb Dept of Management Science and Technology}\\
+   \affaddr{Athens University of Economics and Business}\\
+   \affaddr{Athens, Greece}\\
+   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
   \end{tabular}

### 2015-02-23 msr.tex
finalised authors
some changes / thoughts

@@
 
-\title{Generating the Blueprints of Java Ecosystem}
+\title{Generating the Blueprints of the Java Ecosystem}
 
@@
   Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
+  \begin{tabular}{c}
+   \affaddr{\aueb Dept of Management Science and Technology}\\
+   \affaddr{Athens University of Economics and Business}\\
+   \affaddr{Athens, Greece}\\
+   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
+  \end{tabular}
+  \centering
   \begin{tabular}{cc}
@@
    \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
-  \end{tabular}
-  \centering
-  \begin{tabular}{c}
-   \affaddr{\aueb Dept of Management Science and Technology}\\
-   \affaddr{Athens University of Economics and Business}\\
-   \affaddr{Athens, Greece}\\
-   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
   \end{tabular}
@@
 This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early.
-Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} that have found their way in software development practice and tools.
+Over the years, a wealth of different metrics have appeared in the literature.
+Furthermore, some of them, like Chidamber and Kemerer's~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
+% dimitro@bkarak: provide corresponding refs.
+Also you need to bulk this up.
+A paragraph referring to what we did.
+e.g "In this paper we present a dataset produced by applying three tools on all versions of a snapshot of the Maven repository.
+[...]".
 
@@
 \label{sec:data}
+
+% dimitro@bkarak: This section *does not* present the dataset.
+It presents Maven.
+You should rename the section to "Dataset Construction Process" and merge it with the upcoming one.
+It should go like this: 1) We got this snapshot and 2) applied these three tools to create what you see in the next section.
+You'll present the experiment and *advertise* the effort.
 
@@
 
-The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications.
+The Java platform exists for more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications.
 The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.
-The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.
+The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as Java Specification Requests ({\sc jsr}s), which are supported by prototype implementations.
 
-In the literature, it is referred that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}.
+In the literature, it is suggested that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}.
 This thesis focuses on practical research aspects as well as with the theoretical ones; thus the first problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects.
@@
 
-The initial goal of this experiment was simply to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account.
+The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account.
 Build files or other resources that may contain {\sc dsl}s were not included.
@@
 In publication \cite{MKLGS14}, Mitropoulos et al.
-also experimented in a similar way, by running the findbugs~\cite{HP04} security and bugs audit tool on a large part of the maven repository.
-Our work differs from these these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.
+also experimented in a similar way, by running the FindBugs~\cite{HP04} tool on a large part of the maven repository.
+Our work differs from these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.
 

### 2015-02-23 msr.tex
minor edits
added clmt publication

@@
 Furthermore, some of them, like Chidamber and Kemerer's~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
+
+In this paper, we present a dataset that contains popular metrics, focusing on providing calculation for a large collection of the Java ecosystem.
+For this purpose we selected the maven~\cite{MAVEN} repository.
+The tools that provided the metrics are well-known.
+
 % dimitro@bkarak: provide corresponding refs.
@@
 
-\section{Dataset Contents}
+\section{Dataset Construction Process}
 \label{sec:data}
@@
 
-  \item \textbf{CLMT} \textit{(clmt)} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
+  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
 \end{itemize}

### 2015-02-25 msr.tex
updated msr.tex
adding lots of text

@@
 For this purpose we selected the maven~\cite{MAVEN} repository.
-The tools that provided the metrics are well-known.
+The tools that were used are the \textit{ckjm} \cite{Spi05g}, \textit{jdepend}~\cite{JDEPEND}, and \textit{clmt}~\cite{SGKL09}.
+These tools focus on three main aspects of a software system; object-oriented design, program size, and package design.
 
-% dimitro@bkarak: provide corresponding refs.
-Also you need to bulk this up.
-A paragraph referring to what we did.
-e.g "In this paper we present a dataset produced by applying three tools on all versions of a snapshot of the Maven repository.
-[...]".
+The rest of the paper is structured as follows; first, the datasert construction process is presented and analysed.
+Then we analyse the schema of the database.
+Along with the dataset limitations, we present examples and ideas of basic experimentation with the measurements.
 
@@
 \end{table}
-
-\section{The Three Tools}
 
@@
 
+This dataset followed a narrow selection process, identifying and analysing only projects that were written in Java and had the source code and the binary jar available in the repository.
+The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary jar.
+Since only \textit{clmt} analyses the source code, this ended in drastically reduction of measurements that were exposing object-oriented and package design issues.
+
+In addition, only one version was analysed per project.
+Usually, the latest, which was replaced by a prior version, only if it was violating the aforementioned selection process.
+This decision rendered the dataset unusable, for research focused on evolutionary changes of a software project.
+
 \section{Related Work}
@@
 Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements.
-In publication \cite{MKLGS14}, Mitropoulos et al.
+
+In reference \cite{MKLGS14}, Mitropoulos et al.
 also experimented in a similar way, by running the FindBugs~\cite{HP04} tool on a large part of the maven repository.
@@
 \label{sec:conc}
+
+This dataset is a source of measurements for a large selection of projects, covering the basic scopes of software design, with metrics covering from program size to object-oriented design.
+In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the maven repository.
+In addition, our selection process should be more elastic, allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.
+
+Finally, all versions for each project should also be included, allowing researchers to include the dataset to approaches that focusing on the evolutionary aspect of a software package.
 

### 2015-02-25 msr.tex
reading/writing stuff

@@
 \label{sec:data}
-
-% dimitro@bkarak: This section *does not* present the dataset.
-It presents Maven.
-You should rename the section to "Dataset Construction Process" and merge it with the upcoming one.
-It should go like this: 1) We got this snapshot and 2) applied these three tools to create what you see in the next section.
-You'll present the experiment and *advertise* the effort.
 
@@
 The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.
-The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as Java Specification Requests ({\sc jsr}s), which are supported by prototype implementations.
 
-In the literature, it is suggested that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}.
-This thesis focuses on practical research aspects as well as with the theoretical ones; thus the first problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects.
+By using the dataset, one small problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects.
 In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.

### 2015-02-26 msr.tex
better intro. Concerns in comments.

@@
 Software metrics provide a means to extract useful and measurable information about the structure of a software system.
-Since software artifacts consist of digital data, many of their aspects are easily measured.
-This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early.
+Since software artifacts consist of digital data, many of their aspects can be easily measured.
+This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code).
 Over the years, a wealth of different metrics have appeared in the literature.
-Furthermore, some of them, like Chidamber and Kemerer's~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
+In addition, many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
 
-In this paper, we present a dataset that contains popular metrics, focusing on providing calculation for a large collection of the Java ecosystem.
-For this purpose we selected the maven~\cite{MAVEN} repository.
-The tools that were used are the \textit{ckjm} \cite{Spi05g}, \textit{jdepend}~\cite{JDEPEND}, and \textit{clmt}~\cite{SGKL09}.
-These tools focus on three main aspects of a software system; object-oriented design, program size, and package design.
+In this paper, we present a dataset that contains popular metrics, calculated from the analysis of a large collection of Java projects.
+All projects were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
+Maven is a build automation tool used mostly for Java projects.
+To build a software component, it dynamically downloads Java libraries and Maven plug-ins from the Maven central repository, and stores them in a local cache.
+The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
+Note that this repository has been previously analyzed by researchers to produce relevant datasets as we discuss in Section~\ref{sec:rel}.
+To analyze the projects coming from this repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}.
+All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design.
 
-The rest of the paper is structured as follows; first, the datasert construction process is presented and analysed.
+% dimitro@bkarak: say *WHY* these are important metrics.
+Say something like: "These metrics are important for developers and / or developers because [...]" Provide an example and a reference to show how they saved the universe.
+
+In this paper we present: a) the construction process to
+obtain the collection of the metrics results that the three aforementioned tools produced for {\bf (dimitro@bkarak: put the number of {\sc jar}s here)} {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
+
+% The rest of the paper is structured as follows; first, the dataset construction process is presented and analysed.
 Then we analyse the schema of the database.
@@
 
-Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}.
+% Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}.
 To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}.
@@
 These languages include Java, Clojure, Groovy, and Scala.
+
+% dimitro@bkarak: *Major Concern*: You are not "selling" this right.
+These are bullets.
+You need to show that we put some effort to extract the results.
+Recall our previous data paper.
+You only mention the data cleaning part here.
+What happened when you got the JARs you wanted?
+You run the three tools?
+*How*?
+You need to show it.
+How did you automate this?
+The whole procedure.
+Something like the following: "Once we had the list with the project versions we run the above tools for 4000050 days by using a heavy metal script on one trillion machines."
 
@@
 Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus.
-It included 12,959 projects, with more than 110 million lines of code.
-Overall the dataset contains almost 33 million unique measurements.
+It included 12,959 projects, % dimitro@bkarak: this is a different number from the one at the table.
+with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.
 
@@
 Figure~\ref{fig:database-schema} illustrates the database schema.
-The data are stored in a straightforward manner.
+The data were stored in a straightforward manner.
 The database schema consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
 The central table is \textit{measurement}, which holds the actual measurement values.
-The other tables are used as normalisation tables.
+The other tables are used as normalization tables.
 
-Metrics are divided in six categories that defined its scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}.
+Metrics are divided into six categories that defined its scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}.
 These values are stored in \textit{category} table.
@@
 The descriptive names for each metric are stored in the \textit{measurement\_type} table.
+% dimitro@bkarak: this is not the right way to reference tables. Which table is it? 5? 6? Same below.
 There are 65 metrics available in the dataset.
 The names are composed by the actual metric name and the tool that was used to calculate them e.g.
-\textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the clmt tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the ckjm tool.
+\textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the {\sc clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the {\sc ckjm} tool.
 
@@
 
-The Java platform exists for more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications.
+The Java platform exists for more than a decade and provides a development environment for several application areas, such as the web, grid computing, and traditional client-server applications.
+% dimitro@bkarak: references here.
 The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.
+
+% dimitro@bkarak: I cannot see the connection of the above paragraph with the following.
 
@@
 
-The methodology was the following; A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
+The methodology was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
 \textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used.

### 2015-02-26 msr.tex
added import-process illustration

@@
 
-Initially, a snapshot (January 2012) of the Maven repository was downloaded locally.
+The dataset construction process is illustrated in Figure~\cite{}.
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.5]{import-process}
+\caption{}
+\end{figure}
+
+Initially, a snapshot of the Maven repository was downloaded locally.
 The repository contains various projects and their releases.
@@
 Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus.
-It included 12,959 projects, % dimitro@bkarak: this is a different number from the one at the table.
-with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.
+It included 11,365 projects, with more than 110 million lines of code.
+Overall the dataset contains almost 33 million unique measurements.
 

### 2015-02-26 msr.tex
adding the import process

@@
 
-% dimitro@bkarak: say *WHY* these are important metrics.
-Say something like: "These metrics are important for developers and / or developers because [...]" Provide an example and a reference to show how they saved the universe.
-
-In this paper we present: a) the construction process to
-obtain the collection of the metrics results that the three aforementioned tools produced for {\bf (dimitro@bkarak: put the number of {\sc jar}s here)} {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
-
-% The rest of the paper is structured as follows; first, the dataset construction process is presented and analysed.
-Then we analyse the schema of the database.
-Along with the dataset limitations, we present examples and ideas of basic experimentation with the measurements.
+In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
 
@@
 
-% Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}.
+Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}.
 To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}.
@@
 
-% dimitro@bkarak: *Major Concern*: You are not "selling" this right.
-These are bullets.
-You need to show that we put some effort to extract the results.
-Recall our previous data paper.
-You only mention the data cleaning part here.
-What happened when you got the JARs you wanted?
-You run the three tools?
-*How*?
-You need to show it.
-How did you automate this?
-The whole procedure.
-Something like the following: "Once we had the list with the project versions we run the above tools for 4000050 days by using a heavy metal script on one trillion machines."
-
-The dataset construction process is illustrated in Figure~\cite{}.
-
 \begin{figure}
@@
 \includegraphics[scale=0.5]{import-process}
-\caption{}
+\caption{The dataset construction process}
+\label{fig:dataset-construction}
 \end{figure}
 
+The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}.
 Initially, a snapshot of the Maven repository was downloaded locally.
@@
 The Maven repository contains several versions of each project.
+All versions were filtered out and only the latest was kept.
+Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code.
+The
 
-All versions were filtered out and only the latest was kept.
-For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code.
 Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus.
@@
 
-The descriptive names for each metric are stored in the \textit{measurement\_type} table.
-% dimitro@bkarak: this is not the right way to reference tables. Which table is it? 5? 6? Same below.
+The descriptive names for each metric are stored in the \textit{measurement\_type} database table.
 There are 65 metrics available in the dataset.

### 2015-02-26 msr.tex
updated msr.tex

@@
 
-In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
+In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730} {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
 
@@
 The repository contains various projects and their releases.
-A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}.
-The Maven repository contains several versions of each project.
+We identified only the Java projects.
+The repository contains several versions of each project.
 All versions were filtered out and only the latest was kept.
 Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code.
-The
+We
 

### 2015-02-26 msr.tex
added research opportunities

@@
 
+\section{Research Opportunities}
+\label{sec:research-opportunities}
+
 \section{Experimenting with the Dataset}
 \label{sec:dsl}
-
-The Java platform exists for more than a decade and provides a development environment for several application areas, such as the web, grid computing, and traditional client-server applications.
-% dimitro@bkarak: references here.
-The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}.
-
-% dimitro@bkarak: I cannot see the connection of the above paragraph with the following.
-
-By using the dataset, one small problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects.
-In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.
 

### 2015-02-26 msr.tex
working on text

@@
 Software metrics provide a means to extract useful and measurable information about the structure of a software system.
-Since software artifacts consist of digital data, many of their aspects can be easily measured.
+Software development artifacts consist of digital data, many of their aspects can be easily measured.
 This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code).
 Over the years, a wealth of different metrics have appeared in the literature.
-In addition, many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
+Many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
 
@@
 
-Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation~\cite{MAVEN}.
+Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}.
 To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}.
-The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis.
+The central repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as their runtime environment.
 These languages include Java, Clojure, Groovy, and Scala.
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[scale=0.5]{import-process}
+\includegraphics[scale=0.7]{import-process}
 \caption{The dataset construction process}
 \label{fig:dataset-construction}
-\end{figure}
+\end{figure*}
 
@@
 Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code.
-We
+The projects that did not had both binary and source jars, were excluded from the experiment.
+
+When the selection process was finished, the {\sc jars} were downloaded from the central repository and with the help of a queue, delivered into a series of workers, which executed the tools and provided a series of measurements stored in {\sc json} form.
+The result files were validated by scripts and then the data were imported in a MySQL database.
 
@@
 
-Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
-Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
-Several metrics are calculated by more than one tools in this dataset, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
-Both calculation are stored and provided by the dataset.Three tools were selected.
+Three tools were selected to calculate the measurements.
 
@@
 \end{itemize}
+
+Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
+Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
+Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
+Both calculations are available in the database.
+
+A series of secondary metrics are also stored in the database.
+For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project.
+These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted.
+In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset anf therefore for the Java ecosystem in general.
 
@@
 Figure~\ref{fig:database-schema} illustrates the database schema.
-The data were stored in a straightforward manner.
-The database schema consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
-The central table is \textit{measurement}, which holds the actual measurement values.
-The other tables are used as normalization tables.
+It consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
+The central database table is \textit{measurement}, which holds the measurement values.
+The other tables are used for normalization.
 
-Metrics are divided into six categories that defined its scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}.
-These values are stored in \textit{category} table.
+Metrics are divided into six categories that define their scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}.
+These values are stored in \textit{category} database table.
 
@@
 The names are composed by the actual metric name and the tool that was used to calculate them e.g.
-\textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the {\sc clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the {\sc ckjm} tool.
+\textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.
 
-Filenames, method, class and package names along with other identifiers are stored in the \textit{identifiers} table.
-Note that each measurement has a related filename and a related identifier that points to the software element that is related e.g.
+Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table.
+Note that each measurement has a related filename and a related identifier that points to a software element e.g.
 the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related with the identifier \textit{com.scalagent.jmx}.
 
-Finally the table \textit{project} contains the related project identifiers, extracted from the maven repository.
+Finally, the database table \textit{project} contains the related project identifiers, extracted from the maven repository.
 
@@
 
+The measurements provided by this dataset, can be exploited in many
+
 \section{Experimenting with the Dataset}
 \label{sec:dsl}
+
+Along with the
 

### 2015-02-26 msr.tex
working with research opportunities

@@
 \centering
-\includegraphics[scale=0.7]{import-process}
+\includegraphics[scale=0.6]{import-process}
 \caption{The dataset construction process}
@@
 \centering
-\includegraphics[scale=0.7]{database-schema}
+\includegraphics[scale=0.6]{database-schema}
 \caption{The database schema}
@@
 
-The measurements provided by this dataset, can be exploited in many
+The measurements provided by this dataset, can be used both by researchers and practictioners to validate their ideas.
+Researchers can use the data to experiment with new quality models, or just validate them in real projects.
+Practitioners who develop several tools that calculate metrics that already exist in this dataset, can use it to validate that their tools work correctly.
+
+In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for correlations.
 
@@
 
-Along with the
+As aforementioned in the previous sections,
 
@@
 If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}.
-Consequently, if a project has {\sc dsl} count four (4), then it means that four (4) different application libraries were detected during the source code scan.
+Consequently, if a project has {\sc dsl} count four (4), then it means that four different application libraries were detected during the source code scan.
 Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.

### 2015-02-27 msr.tex
one pass

@@
 Software metrics provide a means to extract useful and measurable information about the structure of a software system.
-Software development artifacts consist of digital data, many of their aspects can be easily measured.
+Software development artifacts consist of digital data, thus many of their aspects can be easily measured.
 This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code).
@@
 
-In this paper, we present a dataset that contains popular metrics, calculated from the analysis of a large collection of Java projects.
-All projects were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
+In this paper, we present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java.
+All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
 Maven is a build automation tool used mostly for Java projects.
@@
 The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
-Note that this repository has been previously analyzed by researchers to produce relevant datasets as we discuss in Section~\ref{sec:rel}.
 To analyze the projects coming from this repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}.
@@
 Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}.
-To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}.
-The central repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as their runtime environment.
-These languages include Java, Clojure, Groovy, and Scala.
+To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}.
+The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala.
+All languages use the {\sc jvm} platform as their runtime environment.
 
@@
 Initially, a snapshot of the Maven repository was downloaded locally.
-The repository contains various projects and their releases.
-We identified only the Java projects.
-The repository contains several versions of each project.
-All versions were filtered out and only the latest was kept.
-Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code.
+The repository contains various projects that contain several versions.
+In our experiment, we only used Java projects.
+For every Java project all versions were filtered out and only the latest was kept.
+
+Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code.
 The projects that did not had both binary and source jars, were excluded from the experiment.
 
-When the selection process was finished, the {\sc jars} were downloaded from the central repository and with the help of a queue, delivered into a series of workers, which executed the tools and provided a series of measurements stored in {\sc json} form.
+When the selection process was finished, we created a series of processing tasks based on the containing all the selected {\sc jar}s, and added them to a task queue mechanism.
+Then we executed a number of workers
+% dimitro@bkarak: written in?
+that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system).
+The tools that were applied on every {\sc jar} were the following.
+
+\begin{itemize}
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
+It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
+The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.
+
+  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
+
+  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
+\end{itemize}
+
+% When the selection process was finished, the {\sc jar}s were downloaded from the central repository and with the help of a queue, delivered into a series of workers, which executed the tools and provided a series of measurements stored in {\sc json} form.
 The result files were validated by scripts and then the data were imported in a MySQL database.
-
-Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus.
-It included 11,365 projects, with more than 110 million lines of code.
-Overall the dataset contains almost 33 million unique measurements.
 
@@
 
-Three tools were selected to calculate the measurements.
+Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final corpus we used.
+It included 11,365 projects, with more than 110 million lines of code.
+Overall the dataset contains almost 33 million unique measurements.
 
-\begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
-It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
-The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.
-
-  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
-
-  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
-\end{itemize}
-
-Table~\ref{tbl:selected-metrics} presents the key metrics that are calculated and stored in the dataset.
+Table~\ref{tbl:selected-metrics} presents the key metrics that were calculated and stored in the dataset.
 Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
@@
 
-A series of secondary metrics are also stored in the database.
+% A series of secondary metrics wesre also stored in the database.
 For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project.
 These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted.
+dimitro@bkarak: then why do you mention it?
+
 In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset anf therefore for the Java ecosystem in general.
@@
 Researchers can use the data to experiment with new quality models, or just validate them in real projects.
-Practitioners who develop several tools that calculate metrics that already exist in this dataset, can use it to validate that their tools work correctly.
+Practitioners who develop several tools that calculate metrics that already exist in this dataset, can use it to validate if their tools work correctly.
 
@@
 As aforementioned in the previous sections,
+
+% dimitro@bkarak: yes what?
 
@@
 
-This dataset followed a narrow selection process, identifying and analysing only projects that were written in Java and had the source code and the binary jar available in the repository.
-The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary jar.
+This dataset followed a narrow selection process, identifying and analysing only projects that were written in Java and had the source code and the binary {\sc jar} available in the repository.
+The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary {\sc jar}.
 Since only \textit{clmt} analyses the source code, this ended in drastically reduction of measurements that were exposing object-oriented and package design issues.
@@
 also experimented in a similar way, by running the FindBugs~\cite{HP04} tool on a large part of the maven repository.
-Our work differs from these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.
+Our work differs from these two approaches since it presents the metrics calculated by the three different static analysis tools.
 

### 2015-02-27 msr.tex
abstract - draft

@@
 \begin{abstract}
-
+Examining a large number of software artifacts can provide
+the research community with data regarding quality an design.
+We present a dataset obtained by statically analyzing
+22730 {\sc jar} files taken from the Maven
+central repository ecosystem. For our analysis
+we used three popular static analysis tools
+that calculate metrics regarding object-oriented design,
+program size, and package design.
+The dataset contains the metrics results that every tool
+reports for every selected {\sc jar} of the
+ecosystem. Our dataset can be used to produce interesting
+research results, as we show in specific examples.
 \end{abstract}

### 2015-02-27 msr.tex
Refactor Ch1 and Ch2

@@
   \begin{tabular}{cc}
-   \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
+   \affaddr{} & \affaddr{\columbia Computer Science Department}\\
    \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
    \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
-   \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
+   \email{g.gousios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
   \end{tabular}
@@
 
-Software metrics provide a means to extract useful and measurable information about the structure of a software system.
+% gousiosg: This is MSR -> no need of stating the obvious
+% gousiosg: if you want, write a paragraph saying that science needs badly a dataset like the one you offer
+
+%Software metrics provide a means to extract useful and measurable information about the structure of a software system.
 Software development artifacts consist of digital data, thus many of their aspects can be easily measured.
@@
 
-In this paper, we present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java.
+We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java.
 All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
-Maven is a build automation tool used mostly for Java projects.
+Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}.
+To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}.
+The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala.
+All supported languages use the {\sc jvm} platform as their runtime environment.
 To build a software component, it dynamically downloads Java libraries and Maven plug-ins from the Maven central repository, and stores them in a local cache.
 The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
-To analyze the projects coming from this repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}.
+
+To analyze the projects coming from Maven repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}.
 All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design.
@@
 \label{sec:data}
-
-Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}.
-To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}.
-The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala.
-All languages use the {\sc jvm} platform as their runtime environment.
 
@@
 In our experiment, we only used Java projects.
-For every Java project all versions were filtered out and only the latest was kept.
+For every Java project
+%gousiosg: say how you identified java projects. Previous datasets failed to
+% do this, therefore it is a strong point
+all versions were filtered out and only the latest was kept.
 
@@
 % dimitro@bkarak: written in?
+% gousiosg: ref dimitro's paper and say you followed the same process
 that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system).
@@
 \begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko.
-It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
-The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g}
+%is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It
+calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
+The version of the tool that we used for this experiment can be found in GitHub~\cite{CKJM}.
 
@@
 These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted.
-dimitro@bkarak: then why do you mention it?
+% dimitro@bkarak: then why do you mention it?
+% gousiosg: @dimitro: I agree with your comment. However, identifying the 
+% DSLs is a worthy contribution. @bkarak: I would rephrase and add a description of
+% how you identified the DSLs. Then also mention this in the research
+% opportunities
 
-In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset anf therefore for the Java ecosystem in general.
+In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
 

### 2015-02-27 msr.tex
Some comments here and there

@@
 
-The measurements provided by this dataset, can be used both by researchers and practictioners to validate their ideas.
+The measurements provided by this dataset, can be used both by researchers and practitioners to validate their ideas.
 Researchers can use the data to experiment with new quality models, or just validate them in real projects.
-Practitioners who develop several tools that calculate metrics that already exist in this dataset, can use it to validate if their tools work correctly.
+Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.
+
+% gousiosg: A unique selling point is DSLs and people who want to do research with
+% DSL embedding can use it I would add something here.
 
@@
 Usually, the latest, which was replaced by a prior version, only if it was violating the aforementioned selection process.
-This decision rendered the dataset unusable, for research focused on evolutionary changes of a software project.
+This decision renders the dataset unusable,
+for research focused on software evolution.
 
@@
 This dataset is a source of measurements for a large selection of projects, covering the basic scopes of software design, with metrics covering from program size to object-oriented design.
-In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the maven repository.
+In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the Maven repository.
+%gousiosg: this is like saying that our current selection process is gtp.
+%rephrase
 In addition, our selection process should be more elastic, allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.

### 2015-02-27 msr.tex
updating numbers

--- 2015-02-27 msr.tex
@@
 Project Count & 11,365\\
-File Count & 604,821\\
-Module Count & 72,302\\
-Lines of Code & 110,156,703\\
-Source Lines of Code & 61,246,807\\
-Comment Lines of Code & 36,696,217\\
+File Count & 449,213\\
+Module Count & 59,436\\
+Lines of Code & 74,565,772\\
+Source Lines of Code & 40,921,287\\
+Comment Lines of Code & 25,268,959\\
 Number of Classes & 499,588\\

### 2015-02-27 msr.tex
updated final numbers

@@
 Comment Lines of Code & 25,268,959\\
-Number of Classes & 499,588\\
-Number of Interfaces & 89,145\\
-Number of Enumerations & 12,732\\
+Number of Classes & 370,518\\
+Number of Interfaces & 66,352\\
+Number of Enumerations & 9,879\\
 Measurement Count & 32,844,836\\
@@
 Usually, the latest, which was replaced by a prior version, only if it was violating the aforementioned selection process.
-This decision renders the dataset unusable,
-for research focused on software evolution.
+This decision renders the dataset unusable, for research focused on software evolution.
 

### 2015-02-27 msr.tex
fixing all the comments

@@
 Examining a large number of software artifacts can provide
-the research community with data regarding quality an design.
+the research community with data regarding quality and design.
 We present a dataset obtained by statically analyzing
 22730 {\sc jar} files taken from the Maven
-central repository ecosystem. For our analysis
+central archive, which is the de-facto application library repository for the Java ecosystem. For our analysis
 we used three popular static analysis tools
@@
 ecosystem. Our dataset can be used to produce interesting
-research results, as we show in specific examples.
+research results, such as measure the domain-specific language usage.
 \end{abstract}
@@
 
-% gousiosg: This is MSR -> no need of stating the obvious
-% gousiosg: if you want, write a paragraph saying that science needs badly a dataset like the one you offer
-
-%Software metrics provide a means to extract useful and measurable information about the structure of a software system.
-Software development artifacts consist of digital data, thus many of their aspects can be easily measured.
-This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code).
-Over the years, a wealth of different metrics have appeared in the literature.
-Many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.
-
 We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java.
@@
 All supported languages use the {\sc jvm} platform as their runtime environment.
-To build a software component, it dynamically downloads Java libraries and Maven plug-ins from the Maven central repository, and stores them in a local cache.
+To build a software component, it dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache.
 The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
@@
 File Count & 449,213\\
-Module Count & 59,436\\
+Package Count & 59,436\\
 Lines of Code & 74,565,772\\
@@
 
-% A series of secondary metrics wesre also stored in the database.
-For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project.
-These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted.
-% dimitro@bkarak: then why do you mention it?
-% gousiosg: @dimitro: I agree with your comment. However, identifying the
-% DSLs is a worthy contribution. @bkarak: I would rephrase and add a description of
-% how you identified the DSLs. Then also mention this in the research
-% opportunities
+A series of newly introduced metrics were also stored in the database that count the usage of specific {\sc dsl} application libraries in a software project.
+These are included in the Table~\ref{tbl:selected-metrics} as \textit{DSL Usage Count}.
+
+The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
+\textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used.
+If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}.
+Consequently, if a project has {\sc dsl} count four (4), then it means that four different application libraries were detected during the source code scan.
+Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
+Note that we focused on libraries that were  included as part of the Java {\sc sdk}.
+
+\begin{table}
+\centering
+\caption{List of selected DSL application libraries}
+\label{tbl:dsl-list}
+\begin{tabular}{l l}
+ \hline
+\textbf{DSL} & \textbf{Java Package}\\
+\hline
+Regular Expressions & \verb|java.util.regex|\\
+XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
+SQL & \verb|java.sql| and \verb|javax.sql|\\
+XPath & \verb|java.xml.xpath|\\
+XSLT & \verb|javax.xml.transform|\\
+RTF & \verb|javax.swing.text.rtf|\\
+HTML & \verb|javax.swing.text.html|\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-As aforementioned in the previous sections,
-
-% dimitro@bkarak: yes what?
-
-The methodology was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
-\textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used.
-If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}.
-Consequently, if a project has {\sc dsl} count four (4), then it means that four different application libraries were detected during the source code scan.
-Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
-Note that all these libraries are included as part of the Java {\sc sdk}.
-
-\begin{table}
-\centering
-\caption{List of selected DSL application libraries}
-\label{tbl:dsl-list}
-\begin{tabular}{l l}
- \hline
-\textbf{DSL} & \textbf{Java Package}\\
-\hline
-Regular Expressions & \verb|java.util.regex|\\
-XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
-SQL & \verb|java.sql| and \verb|javax.sql|\\
-XPath & \verb|java.xml.xpath|\\
-XSLT & \verb|javax.xml.transform|\\
-RTF & \verb|javax.swing.text.rtf|\\
-HTML & \verb|javax.swing.text.html|\\
-\hline
-\end{tabular}
-\end{table}
-
 The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account.

### 2015-02-27 msr.tex
updated abstract; intro; dataset construction

@@
 All supported languages use the {\sc jvm} platform as their runtime environment.
-To build a software component, it dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache.
+To build a software component, first by using the maven accompanying tools, dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache.
 The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
@@
 
-In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730} {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
+In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for 22730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
 
@@
 For every Java project
-%gousiosg: say how you identified java projects. Previous datasets failed to
-% do this, therefore it is a strong point
 all versions were filtered out and only the latest was kept.
-
-Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code.
+The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code.
 The projects that did not had both binary and source jars, were excluded from the experiment.
+When the source {\sc jar} file was downloaded, it was scanned for Java source files.
+If source files were present in the archive, then the project was flagged as Java project and considered valid.
 
 When the selection process was finished, we created a series of processing tasks based on the containing all the selected {\sc jar}s, and added them to a task queue mechanism.
-Then we executed a number of workers
-% dimitro@bkarak: written in?
-% gousiosg: ref dimitro's paper and say you followed the same process
-that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system).
+Then we executed a number of workers that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system).
 The tools that were applied on every {\sc jar} were the following.
+The workers were written in Python.
+In addition, there were several shell scripts (bash) that performed several checks and sanitisation tasks.
 
 \begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g}
-%is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It
-calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} that calculates many software metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
 The version of the tool that we used for this experiment can be found in GitHub~\cite{CKJM}.
@@
 \end{itemize}
-
-% When the selection process was finished, the {\sc jar}s were downloaded from the central repository and with the help of a queue, delivered into a series of workers, which executed the tools and provided a series of measurements stored in {\sc json} form.
-The result files were validated by scripts and then the data were imported in a MySQL database.
 
@@
 
-Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final corpus we used.
-It included 11,365 projects, with more than 110 million lines of code.
-Overall the dataset contains almost 33 million unique measurements.
+Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset. It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements.
 
@@
 The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
-\textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used.
-If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}.
-Consequently, if a project has {\sc dsl} count four (4), then it means that four different application libraries were detected during the source code scan.
+\textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project.
 Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
@@
 
-In Section~\ref{sec:dsl}, we describe a small experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
+In Section~\ref{sec:dsl}, we describe an experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
 

### 2015-02-27 msr.tex
added methodology ref
working on experinment

@@
 
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \label{fig:dataset-construction}
-\end{figure*}
+\end{figure}
 
 The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}.
+In general, it follows the same methodology presented in reference \cite{MKLGS14}.
 Initially, a snapshot of the Maven repository was downloaded locally.
@@
 \textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project.
+Build files or other resources that may contain {\sc dsl}s were not included.
+One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.
 Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
@@
 
-Finally, the database table \textit{project} contains the related project identifiers, extracted from the maven repository.
+Finally, the database table \textit{project} contains the related project identifiers, directly extracted from the maven repository.
 
@@
 
-% gousiosg: A unique selling point is DSLs and people who want to do research with
-% DSL embedding can use it I would add something here.
+The dataset includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}.
+These kind of metrics, can be really usefull for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns \cite{KARA14}.
 
-In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for correlations.
+In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations.
 
@@
 
-The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account.
-Build files or other resources that may contain {\sc dsl}s were not included.
-One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.
+The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl} for the Java ecosystem.
+The related metrics can be found in the database table named \textit{measuremnt\_type}, these are: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
+\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
+With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset.
+We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects
 

### 2015-02-27 msr.tex
still working

@@
 \author{
-  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
+  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Georgios Gousios\run \and Diomidis Spinellis\aueb \and Panos Louridas\aueb\\
   \begin{tabular}{c}
@@
    \affaddr{Athens, Greece}\\
-   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
+   \email{\{bkarak,dds,louridas\}@aueb.gr}\\
   \end{tabular}
@@
 \centering
-\includegraphics[scale=0.6]{import-process}
+\includegraphics[scale=0.5]{import-process}
 \caption{The dataset construction process}
@@
 With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset.
-We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects
+We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects (13\%).
+Regular expressions are second most popular with 909 occurrences (7\%).
+Note that these number represents the projects that {\sc xml} and regular expressions were used a sole {\sc dsl}s.
 
@@
 \centering
-\caption{Popular DSL Usage Combinations}
+\caption{DSL Usage Combinations Ranking}
 \label{tbl:dsl-top-usage}

### 2015-02-27 msr.tex
the big table is now broken in 4; layout is much better

@@
 \centering
-\includegraphics[scale=0.5]{import-process}
+\includegraphics[scale=0.45]{import-process}
 \caption{The dataset construction process}
@@
 
-Table~\ref{tbl:selected-metrics} presents the key metrics that were calculated and stored in the dataset.
+Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset.
 Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
@@
 A series of newly introduced metrics were also stored in the database that count the usage of specific {\sc dsl} application libraries in a software project.
-These are included in the Table~\ref{tbl:selected-metrics} as \textit{DSL Usage Count}.
-
-The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
+These are included in the Table~\ref{tbl:size-selected-metrics}.
+The methodology to identify and calculate the {\sc dsl} metrics is the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
 \textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project.
@@
 \centering
-\caption{Key Metrics}
-\label{tbl:selected-metrics}
+\caption{Class Design Metrics}
+\label{tbl:class-selected-metrics}
 \begin{tabular}{l l}
@@
 \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Method Design Metrics}
+\label{tbl:method-selected-metrics}
+\begin{tabular}{l l}
+ \hline
 \multicolumn{2}{l}{\textit{\textbf{Method Design}}}\\
@@
 McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Method Design Metrics}
+\label{tbl:package-selected-metrics}
+\begin{tabular}{l l}
  \hline
@@
 Distance Main Sequence & \textit{jdep}\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Program Size Metrics}
+\label{tbl:size-selected-metrics}
+\begin{tabular}{l l}
  \hline
@@
 DSL Usage Count & \textit{clmt}\\
+RTF Usage Count & \textit{clmt}\\
+Regex Usage Count & \textit{clmt}\\
+HTML Usage Count & \textit{clmt}\\
+XPath Usage Count & \textit{clmt}\\
+XSLT Usage Count & \textit{clmt}\\
+XML Usage Count & \textit{clmt}\\
+SQL Usage Count & \textit{clmt}\\
 File Count & \textit{clmt}\\
@@
 \centering
-\includegraphics[scale=0.6]{database-schema}
+\includegraphics[scale=0.5]{database-schema}
 \caption{The database schema}
@@
 The dataset includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}.
-These kind of metrics, can be really usefull for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns \cite{KARA14}.
+These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns \cite{KARA14}.
 
@@
 \label{sec:dsl}
-
-The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl} for the Java ecosystem.
-The related metrics can be found in the database table named \textit{measuremnt\_type}, these are: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
-\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
-With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset.
-We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects (13\%).
-Regular expressions are second most popular with 909 occurrences (7\%).
-Note that these number represents the projects that {\sc xml} and regular expressions were used a sole {\sc dsl}s.
 
@@
 XML, XPath & 50\\
-XML, XPath, XSLT & 39\\
-Regex, XML, XPath, XSLT & 38\\
-HTML & 23\\
-Regex, XML, XPath & 20\\
-Regex, SQL, XML, XPath, XSLT & 18\\
-SQL, XML, XPath, XSLT & 11\\
-HTML, Regex, XML & 10\\
-HTML, XML & 10\\
 \hline
@@
 \end{table}
+
+The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl} for the Java ecosystem.
+The related metrics can be found in the database table named \textit{measuremnt\_type}, these are: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
+\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
+With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset.
+We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects (13\%).
+Regular expressions are second most popular with 909 occurrences (7\%).
+Note that these number represents the projects that {\sc xml} and regular expressions were used as sole {\sc dsl}.
 

### 2015-02-27 msr.tex
fixed scale on database schema figure
almost there

@@
 \centering
-\includegraphics[scale=0.5]{database-schema}
+\includegraphics[scale=0.7]{database-schema}
 \caption{The database schema}
@@
 
-This dataset followed a narrow selection process, identifying and analysing only projects that were written in Java and had the source code and the binary {\sc jar} available in the repository.
+This dataset adopted a narrow selection process, identifying and analysing only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository.
 The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary {\sc jar}.

### 2015-02-27 msr.tex
working on conclusions; related

@@
 
-In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations.
+In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations, since these dataset also analysed projects from the Maven repository.
 
@@
 Regular expressions are second most popular with 909 occurrences (7\%).
-Note that these number represents the projects that {\sc xml} and regular expressions were used as sole {\sc dsl}.
+Note that these number represents the projects that {\sc xml} and regular expressions were used as the only {\sc dsl}.
 
@@
 In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the Maven repository.
-%gousiosg: this is like saying that our current selection process is gtp.
-%rephrase
-In addition, our selection process should be more elastic, allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.
+
+Currently, the selection process was strict, filtering out projects that did not have a binary and a source {\sc jar}.
+In the future, we consider allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.
+This will allow to expand our project coverage on the Maven repository.
 

### 2015-02-27 msr.tex
fixed category; keywords; terms
changes in intro

@@
 
-\category{D.2.4}{Software Engineering}{Software/Program Verification}[Statistical methods]
+\category{D.2.8}{Software Engineering}{Metrics}[Product metrics]
 
-\terms{Static Analysis, Software Ecosystems.}
+\terms{Static Analysis, Software Metrics}
 
-\keywords{JDepend, Software Metrics, Chidamber and Kemerer.}
+\keywords{Java, Software Metrics, Chidamber and Kemerer, Maven}
 
@@
 All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
+
 Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}.
@@
 All supported languages use the {\sc jvm} platform as their runtime environment.
-To build a software component, first by using the maven accompanying tools, dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache.
+To build a software component, it dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache.
 The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
@@
 All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design.
+Such aspects are considered very important because they provide quantifiable information about the quality and structure of a software component.
 

### 2015-02-28 msr.tex
changes in Section 2

@@
 
-The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}.
-In general, it follows the same methodology presented in reference \cite{MKLGS14}.
+The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology presented in reference \cite{MKLGS14}.
+
 Initially, a snapshot of the Maven repository was downloaded locally.
@@
 In our experiment, we only used Java projects.
-For every Java project
-all versions were filtered out and only the latest was kept.
+For every Java project all versions were filtered out and only the latest was kept.
 The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code.
-The projects that did not had both binary and source jars, were excluded from the experiment.
+The projects that did not had both binary and source {\sc jar}s, were excluded from the experiment.
 When the source {\sc jar} file was downloaded, it was scanned for Java source files.
-If source files were present in the archive, then the project was flagged as Java project and considered valid.
+If the source files were present in the archive, then the project was flagged as a valid Java project.
 
-When the selection process was finished, we created a series of processing tasks based on the containing all the selected {\sc jar}s, and added them to a task queue mechanism.
+When the selection process was finished, we created a series of processing tasks based on the selected {\sc jar}s, and added them to a task queue mechanism.
 Then we executed a number of workers that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system).
-The tools that were applied on every {\sc jar} were the following.
 The workers were written in Python.
-In addition, there were several shell scripts (bash) that performed several checks and sanitisation tasks.
+In addition, there were several shell scripts (bash) that performed several checks and sanitisation tasks (e.g.
+checking for malformed results).
+The tools that were applied on every {\sc jar} were the following:
 
 \begin{itemize}
-  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} that calculates many software metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g}; which calculates many software metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
 The version of the tool that we used for this experiment can be found in GitHub~\cite{CKJM}.
 
-  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
+  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND}; a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
 
-  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09} stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
+  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09}; which stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
 \end{itemize}
@@
 
-Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset. It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements.
-
+Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset.
+It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements.
 Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset.
@@
 
-A series of newly introduced metrics were also stored in the database that count the usage of specific {\sc dsl} application libraries in a software project.
-These are included in the Table~\ref{tbl:size-selected-metrics}.
-The methodology to identify and calculate the {\sc dsl} metrics is the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g.
-\textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project.
+% dimitro@bkarak: enrich the above with refs. The ref section is poor. e.g. [...] focuses on object-oriented design metrics *citation here* [...].
+
+A series of newly introduced metrics were also stored in the database.
+Such metrics can count the usage of specific {\sc dsl} application libraries in a software project and they are included in the Table~\ref{tbl:size-selected-metrics}.
+The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements (e.g.
+\textit{java.util.regex}).
+These statements indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project.
 Build files or other resources that may contain {\sc dsl}s were not included.
-One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.
+One final assumption was also made; if {\sc xp}ath or {\sc xslt} were found in the source code, then the project would be marked as a project that utilizes {\sc xml}.
+This is because both languages are used for query and transformations on {\sc xml} {\sc dom} trees.
 Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
@@
 
-In Section~\ref{sec:dsl}, we describe an experiment based on these metrics that measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
+In Section~\ref{sec:dsl}, we describe an experiment based on these metrics. The experiment measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
 

### 2015-02-28 msr.tex
changes in 3

@@
 Figure~\ref{fig:database-schema} illustrates the database schema.
-It consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
+Specifically, it consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
 The central database table is \textit{measurement}, which holds the measurement values.
-The other tables are used for normalization.
+The other tables can be used for normalization.
 
@@
 There are 65 metrics available in the dataset.
-The names are composed by the actual metric name and the tool that was used to calculate them e.g.
-\textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity from the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.
+The names are composed by the actual metric name and the tool that was used to calculate them.
+For instance, \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity generated by the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.
 
 Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table.
-Note that each measurement has a related filename and a related identifier that points to a software element e.g.
-the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related with the identifier \textit{com.scalagent.jmx}.
-
+Note that each measurement has a related filename and a related identifier that points to a software element.
+For example the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related to the identifier \textit{com.scalagent.jmx}.
 Finally, the database table \textit{project} contains the related project identifiers, directly extracted from the maven repository.

### 2015-02-28 msr.tex
added refs

--- 2015-02-28 msr.tex
@@
 Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset.
-Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
-Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity}, which is calculated by both \textit{clmt} and \textit{ckjm}.
+Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics \cite{LOKI94}, \cite{CHKE94}, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
+Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity} \cite{cabe76}, which is calculated by both \textit{clmt} and \textit{ckjm}.
 Both calculations are available in the database.
-
-% dimitro@bkarak: enrich the above with refs. The ref section is poor. e.g. [...] focuses on object-oriented design metrics *citation here* [...].
 

### 2015-02-28 msr.tex
fixed bad caption
Section 4 - pass

@@
 \centering
-\caption{Method Design Metrics}
+\caption{Package Design Metrics}
 \label{tbl:package-selected-metrics}
@@
 
-The measurements provided by this dataset, can be used both by researchers and practitioners to validate their ideas.
-Researchers can use the data to experiment with new quality models, or just validate them in real projects.
+The measurements provided by our dataset, can be used by researchers and practitioners alike.
+Researchers can use the data to experiment with new quality models, or validate them in real projects.
 Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.
 
-The dataset includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}.
-These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns \cite{KARA14}.
+The dataset also includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}.
+These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section.
 
-In addition, this dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations, since these dataset also analysed projects from the Maven repository.
+Finally, our dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations.
+This is because their datasets were also produced by analyzing projects coming from the Maven repository.
 

### 2015-02-28 msr.tex
section 5

@@
 
-The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl} for the Java ecosystem.
-The related metrics can be found in the database table named \textit{measuremnt\_type}, these are: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
+The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects.
+The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
 \textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
-With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}, which lists popular {\sc dsl} usage combinations for the dataset.
-We see that {\sc xml} is the big winner with 1561 occurrences in 11365 projects (13\%).
-Regular expressions are second most popular with 909 occurrences (7\%).
-Note that these number represents the projects that {\sc xml} and regular expressions were used as the only {\sc dsl}.
+With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}.
+This table, lists popular {\sc dsl} usage combinations found in our dataset.
+An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1561 occurrences in 11365 projects (13\%).
+Regular expressions are also popular with 909 occurrences (7\%).
+Note that the numbers represents the projects where {\sc xml} and regular expressions were used as the only {\sc dsl}.
 

### 2015-02-28 msr.tex
minor fix
removed headers from tables
several minor fixes

@@
 \hline
-\multicolumn{2}{l}{\textit{\textbf{Class Design}}}\\
-\hline
 Depth Of Inheritance Tree & \textit{ckjm}\\
@@
 \hline
-\multicolumn{2}{l}{\textit{\textbf{Method Design}}}\\
-\hline
 Number of Method Parameters & \textit{clmt}\\
@@
 \begin{tabular}{l l}
- \hline
-\multicolumn{2}{l}{\textit{\textbf{Package Design}}}\\
 \hline
@@
 \begin{tabular}{l l}
- \hline
-\multicolumn{2}{l}{\textit{\textbf{Program Size Metrics}}}\\
  \hline
@@
 The measurements provided by our dataset, can be used by researchers and practitioners alike.
-Researchers can use the data to experiment with new quality models, or validate them in real projects.
-Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools work correctly.
+Researchers can use the data to experiment with new software quality models, or validate them with real projects.
+Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools produce correct results.
 
@@
 \centering
-\caption{DSL Usage Combinations Ranking}
+\caption{Top DSL Usage Combinations}
 \label{tbl:dsl-top-usage}
@@
 The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects.
-The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
-\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
-With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}.
+The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage}, \textit{RegexUsage}, \textit{HTMLUsage}, \textit{HTMLUsage}, \textit{XPathUsage}, \textit{XSLTUsage}, \textit{XMLUsage}, \textit{SQLUsage}, and \textit{DSLCount}.
+A Python script that analysed the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}.
 This table, lists popular {\sc dsl} usage combinations found in our dataset.
-An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1561 occurrences in 11365 projects (13\%).
+An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1,561 occurrences in 11,365 projects (13\%).
 Regular expressions are also popular with 909 occurrences (7\%).

### 2015-02-28 msr.tex
formatting a number

@@
 
-In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for 22730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
+In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for 22,730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
 

### 2015-02-28 msr.tex
6 and 7

--- 2015-02-28 msr.tex
@@
 \includegraphics[scale=0.45]{import-process}
-\caption{The dataset construction process}
+\caption{The dataset construction process.}
 \label{fig:dataset-construction}
@@
 \centering
-\caption{The selected Maven projects' size metrics}
+\caption{The selected Maven projects' size metrics.}
 \label{tbl:oss-size-metrics}
@@
 \centering
-\caption{List of selected DSL application libraries}
+\caption{List of selected {\sc dsl} application libraries.}
 \label{tbl:dsl-list}
@@
 \centering
-\caption{Class Design Metrics}
+\caption{Class Design Metrics.}
 \label{tbl:class-selected-metrics}
@@
 \centering
-\caption{Method Design Metrics}
+\caption{Method Design Metrics.}
 \label{tbl:method-selected-metrics}
@@
 \centering
-\includegraphics[scale=0.7]{database-schema}
-\caption{The database schema}
+\includegraphics[scale=0.65]{database-schema}
+\caption{The database schema.}
 \label{fig:database-schema}
@@
 \centering
-\caption{DSL Usage Combinations Ranking}
+\caption{{\sc dsl} Usage Combinations Ranking.}
 \label{tbl:dsl-top-usage}
@@
 \textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
-With a python script that analyses the measurements stored in the database, we produced Table~\ref{tbl:dsl-top-usage}.
+With a python script that analyses the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}.
 This table, lists popular {\sc dsl} usage combinations found in our dataset.
@@
 
-This dataset adopted a narrow selection process, identifying and analysing only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository.
-The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary {\sc jar}.
-Since only \textit{clmt} analyses the source code, this ended in drastically reduction of measurements that were exposing object-oriented and package design issues.
+As we mentioned earlier, to produce our dataset we adopted a narrow selection process.
+In particular, we identified and analyzed only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository.
+The latter reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}.
+Since only \textit{clmt} analyses the source code, this resulted in the reduction of the number of measurements that exposed object-oriented and package design issues.
 
-In addition, only one version was analysed per project.
-Usually, the latest, which was replaced by a prior version, only if it was violating the aforementioned selection process.
+Finally, only one version was analyzed per project (the latest, unless it violated the aforementioned restriction).
 This decision renders the dataset unusable, for research focused on software evolution.
@@
 
-In reference \cite{MKLGS14}, Mitropoulos et al.
-also experimented in a similar way, by running the FindBugs~\cite{HP04} tool on a large part of the maven repository.
-Our work differs from these two approaches since it presents the metrics calculated by the three different static analysis tools.
+Also, Mitropoulos et al.
+performed a similar experiment~\cite{MKLGS14}.
+In particular, they used the FindBugs~\cite{HP04} static analysis tool, to analyze a large part of the maven repository.
+Their dataset includes for each {\sc jar}, a corresponding bug collection produced by FindBugs.
+Our work differs from these two approaches since it presents the metrics calculated by the three different static analysis tools that calculate metrics regarding object-oriented design, program size, and package design.
 

### 2015-02-28 msr.tex
removed garbage

@@
 \centering
-\caption{{\sc dsl} Usage Combinations Ranking.}
+\caption{Top {\sc dsl} Usage Combinations}
 \label{tbl:dsl-top-usage}
@@
 The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects.
-The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage\_clmt}, \textit{RegexUsage\_clmt},
-\textit{HTMLUsage\_clmt}, \textit{HTMLUsage\_clmt}, \textit{XPathUsage\_clmt}, \textit{XSLTUsage\_clmt}, \textit{XMLUsage\_clmt}, \textit{SQLUsage\_clmt}, and \textit{DSLCount\_clmt}.
-With a python script that analyses the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}.
+The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage}, \textit{RegexUsage}, \textit{HTMLUsage}, \textit{HTMLUsage}, \textit{XPathUsage}, \textit{XSLTUsage}, \textit{XMLUsage}, \textit{SQLUsage}, and \textit{DSLCount}.
+A Python script that analysed the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}.
 This table, lists popular {\sc dsl} usage combinations found in our dataset.
-An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1561 occurrences in 11365 projects (13\%).
+An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1,561 occurrences in 11,365 projects (13\%).
 Regular expressions are also popular with 909 occurrences (7\%).

### 2015-02-28 msr.tex
changes in the final section

@@
 22730 {\sc jar} files taken from the Maven
-central archive, which is the de-facto application library repository for the Java ecosystem. For our analysis
+central archive, which is the de-facto application library
+repository for the Java ecosystem. For our analysis
 we used three popular static analysis tools
@@
 \centering
-\caption{Package Design Metrics}
+\caption{Package Design Metrics.}
 \label{tbl:package-selected-metrics}
@@
 \centering
-\caption{Program Size Metrics}
+\caption{Program Size Metrics.}
 \label{tbl:size-selected-metrics}
@@
 \centering
-\caption{Top {\sc dsl} Usage Combinations}
+\caption{Top {\sc dsl} Usage Combinations.}
 \label{tbl:dsl-top-usage}
@@
 
-This dataset is a source of measurements for a large selection of projects, covering the basic scopes of software design, with metrics covering from program size to object-oriented design.
-In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates of the Maven repository.
+We presented a dataset created by applying three different static analysis tools on Java projects coming from the Maven Central repository.
+The results invlove a variety of software metrics from program size to object-oriented design.
+%In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates made in the repository.
+We have also shown how our data can be used to extract meaningful results concerning {\sc dsl} usage in Java Projects.
 
-Currently, the selection process was strict, filtering out projects that did not have a binary and a source {\sc jar}.
-In the future, we consider allowing the participation of projects, that cannot be analysed by all the tools, due to source code unavailability.
-This will allow to expand our project coverage on the Maven repository.
-
-Finally, all versions for each project should also be included, allowing researchers to include the dataset to approaches that focusing on the evolutionary aspect of a software package.
+As we discussed, our selection process was strict, filtering out projects that did not have the project's sources.
+However, we are planning to expand our project coverage in the future and include projects that cannot be analysed by all tools (due to source code unavailability).
+Finally, by including all versions for each project we can allow researchers to use our dataset in the evolution context.
 

### 2015-03-29 msr2015-camera-ready.tex
bootstraping camera-ready

%% This style is provided for the ICSE 2015 main conference,
%% ICSE 2015 co-located events, and ICSE 2015 workshops.

%% bare_conf_ICSE15.tex
%% V1.4
%% 2014/05/22

%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Generating the Blueprints of the Java Ecosystem}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Michael Shell}
%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: http://www.michaelshell.org/contact.html}
%\and
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
Homer Simpson\IEEEauthorrefmark{2},
James Kirk\IEEEauthorrefmark{3},
Montgomery Scott\IEEEauthorrefmark{3} and
Eldon Tyrell\IEEEauthorrefmark{4}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
Georgia Institute of Technology,
Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
Email: homer@thesimpsons.com}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
Telephone: (800) 555--1212, Fax: (888) 555--1212}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2015-03-29 msr2015-camera-ready.tex
almost there

@@
 \ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
+  \usepackage[pdftex]{graphicx}
   % declare the path(s) where your graphic files are
@@
 \begin{abstract}
-%\boldmath
-The abstract goes here.
+Examining a large number of software artifacts can provide
+the research community with data regarding quality and design.
+We present a dataset obtained by statically analyzing
+22730 {\sc jar} files taken from the Maven
+central archive, which is the de-facto application library
+repository for the Java ecosystem. For our analysis
+we used three popular static analysis tools
+that calculate metrics regarding object-oriented design,
+program size, and package design.
+The dataset contains the metrics results that every tool
+reports for every selected {\sc jar} of the
+ecosystem. Our dataset can be used to produce interesting
+research results, such as measure the domain-specific language usage.
 \end{abstract}
@@
 \section{Introduction}
-% no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.7 and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
+\label{sec:intro}
 
-\hfill mds
+We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java.
+All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
 
-\hfill January 11, 2007
+Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}.
+To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}.
+The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala.
+All supported languages use the {\sc jvm} platform as their runtime environment.
+To build a software component, it dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache.
+The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+To analyze the projects coming from Maven repository, we used the following tools: a) {\sc ckjm} \cite{Spi05g}, b) {\sc jd}epend~\cite{JDEPEND}, and c) {\sc clmt}~\cite{SGKL09}.
+All tools focus on three main aspects of a software system, namely: object-oriented design, program size, and package design.
+Such aspects are considered very important because they provide quantifiable information about the quality and structure of a software component.
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for 22,730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex,
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
+\section{Dataset Construction Process}
+\label{sec:data}
 
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
+\begin{figure}
+\centering
+\includegraphics[scale=0.45]{import-process}
+\caption{The dataset construction process.}
+\label{fig:dataset-construction}
+\end{figure}
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
+The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology presented in reference \cite{MKLGS14}.
 
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
+Initially, a snapshot of the Maven repository was downloaded locally.
+The repository contains various projects that contain several versions.
+In our experiment, we only used Java projects.
+For every Java project all versions were filtered out and only the latest was kept.
+The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code.
+The projects that did not had both binary and source {\sc jar}s, were excluded from the experiment.
+When the source {\sc jar} file was downloaded, it was scanned for Java source files.
+If the source files were present in the archive, then the project was flagged as a valid Java project.
+
+When the selection process was finished, we created a series of processing tasks based on the selected {\sc jar}s, and added them to a task queue mechanism.
+Then we executed a number of workers that checked out tasks from the queue, applied the static analysis tools on each {\sc jar} and stored the results to the data repository (a {\sc m}y{\sc sql} database system).
+The workers were written in Python.
+In addition, there were several shell scripts (bash) that performed several checks and sanitisation tasks (e.g.
+checking for malformed results).
+The tools that were applied on every {\sc jar} were the following:
+
+\begin{itemize}
+  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g}; which calculates many software metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}.
+The version of the tool that we used for this experiment can be found in GitHub~\cite{CKJM}.
+
+  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND}; a tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
+
+  \item \textbf{CLMT} \textit{(clmt)}~\cite{SGKL09}; which stands for \textit{cross-language metric tool} and analyses the source code of several languages in order to calculate a series of size metrics.
+\end{itemize}
+
+\begin{table}
+\centering
+\caption{The selected Maven projects' size metrics.}
+\label{tbl:oss-size-metrics}
+\begin{tabular}{l r}
+ \hline
+\textbf{Metric} & \textbf{Value}\\
+\hline
+Project Count & 11,365\\
+File Count & 449,213\\
+Package Count & 59,436\\
+Lines of Code & 74,565,772\\
+Source Lines of Code & 40,921,287\\
+Comment Lines of Code & 25,268,959\\
+Number of Classes & 370,518\\
+Number of Interfaces & 66,352\\
+Number of Enumerations & 9,879\\
+Measurement Count & 32,844,836\\
+\hline
+\end{tabular}
+\end{table}
+
+Table \ref{tbl:oss-size-metrics} presents several size metrics for our dataset.
+It includes 11,365 projects, with more than 74 million lines of code and almost 33 million unique measurements.
+Table~\ref{tbl:class-selected-metrics}, \ref{tbl:method-selected-metrics}, \ref{tbl:package-selected-metrics}, and \ref{tbl:size-selected-metrics} present the key metrics that are calculated and stored in the dataset.
+Each tool focuses on a different aspect of a software system; \textit{ckjm} focuses on object-oriented design metrics \cite{LOKI94}, \cite{CHKE94}, \textit{jdepend} on package design, while \textit{clmt} focuses on program size metrics.
+Several metrics are calculated by more than one tool, like \textit{cyclomatic complexity} \cite{cabe76}, which is calculated by both \textit{clmt} and \textit{ckjm}.
+Both calculations are available in the database.
+
+A series of newly introduced metrics were also stored in the database.
+Such metrics can count the usage of specific {\sc dsl} application libraries in a software project and they are included in the Table~\ref{tbl:size-selected-metrics}.
+The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements (e.g.
+\textit{java.util.regex}).
+These statements indicated that the standard package that implements regular expressions was used, thus regular expressions were used in the project.
+Build files or other resources that may contain {\sc dsl}s were not included.
+One final assumption was also made; if {\sc xp}ath or {\sc xslt} were found in the source code, then the project would be marked as a project that utilizes {\sc xml}.
+This is because both languages are used for query and transformations on {\sc xml} {\sc dom} trees.
+Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries.
+Note that we focused on libraries that were included as part of the Java {\sc sdk}.
+
+\begin{table}
+\centering
+\caption{List of selected {\sc dsl} application libraries.}
+\label{tbl:dsl-list}
+\begin{tabular}{l l}
+ \hline
+\textbf{DSL} & \textbf{Java Package}\\
+\hline
+Regular Expressions & \verb|java.util.regex|\\
+XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
+SQL & \verb|java.sql| and \verb|javax.sql|\\
+XPath & \verb|java.xml.xpath|\\
+XSLT & \verb|javax.xml.transform|\\
+RTF & \verb|javax.swing.text.rtf|\\
+HTML & \verb|javax.swing.text.html|\\
+\hline
+\end{tabular}
+\end{table}
+
+In Section~\ref{sec:dsl}, we describe an experiment based on these metrics. The experiment measures the popularity of {\sc dsl} usage for the dataset and therefore for the Java ecosystem in general.
+
+\begin{table}
+\centering
+\caption{Class Design Metrics.}
+\label{tbl:class-selected-metrics}
+\begin{tabular}{l l}
+\hline
+Depth Of Inheritance Tree & \textit{ckjm}\\
+Coupling Between Objects & \textit{ckjm}\\
+Weighted Methods Per Class & \textit{ckjm}\\
+Response For Class & \textit{ckjm}\\
+Lack Of Cohesion In Methods & \textit{ckjm}\\
+Number Of Children & \textit{ckjm}\\
+Attribute Hiding Factor & \textit{clmt}\\
+Coupling Between Methods & \textit{ckjm}\\
+Average Method Complexity & \textit{ckjm}\\
+Cohesion Among Methods of Class & \textit{ckjm}\\
+Data Access Metric & \textit{ckjm, clmt}\\
+Inheritance Coupling & \textit{ckjm}\\
+Lack Of Cohesion In Methods3 & \textit{ckjm}\\
+Measure Of Aggregation & \textit{ckjm}\\
+Measure Of Functional Abstraction & \textit{ckjm}\\
+Number of Attributes & \textit{clmt}\\
+Method Hiding Factor & \textit{clmt}\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Method Design Metrics.}
+\label{tbl:method-selected-metrics}
+\begin{tabular}{l l}
+\hline
+Number of Method Parameters & \textit{clmt}\\
+Number of Methods & \textit{clmt, ckjm}\\
+McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Package Design Metrics.}
+\label{tbl:package-selected-metrics}
+\begin{tabular}{l l}
+\hline
+Number of Concrete Classes & \textit{jdep}\\
+Afferent Couplings & \textit{jdep, ckjm}\\
+Efferent Couplings & \textit{jdep, ckjm}\\
+Instability & \textit{jdep}\\
+Abstractness & \textit{jdep}\\
+Distance Main Sequence & \textit{jdep}\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Program Size Metrics.}
+\label{tbl:size-selected-metrics}
+\begin{tabular}{l l}
+ \hline
+Number of Classes & \textit{clmt, ckjm, jdep}\\
+Number of Enumerations & \textit{clmt, ckjm}\\
+Number of Interfaces & \textit{clmt, ckjm}\\
+Module Count & \textit{clmt, ckjm}\\
+Comments Lines Of Code & \textit{clmt}\\
+Lines Of Code & \textit{clmt, ckjm}\\
+Source Lines Of Code & \textit{clmt}\\
+Function Oriented Code & \textit{clmt}\\
+DSL Usage Count & \textit{clmt}\\
+RTF Usage Count & \textit{clmt}\\
+Regex Usage Count & \textit{clmt}\\
+HTML Usage Count & \textit{clmt}\\
+XPath Usage Count & \textit{clmt}\\
+XSLT Usage Count & \textit{clmt}\\
+XML Usage Count & \textit{clmt}\\
+SQL Usage Count & \textit{clmt}\\
+File Count & \textit{clmt}\\
+\hline
+\end{tabular}
+\end{table}
+
+\section{Database Structure}
+\label{sec:db}
+
+Figure~\ref{fig:database-schema} illustrates the database schema.
+Specifically, it consists of five tables; \textit{measurement}, \textit{category}, \textit{identifiers}, \textit{measurement\_type}, and \textit{project}.
+The central database table is \textit{measurement}, which holds the measurement values.
+The other tables can be used for normalization.
+
+Metrics are divided into six categories that define their scope; \textit{module}, \textit{class}, \textit{method}, \textit{code unit}, and \textit{project-wide}.
+These values are stored in \textit{category} database table.
+
+The descriptive names for each metric are stored in the \textit{measurement\_type} database table.
+There are 65 metrics available in the dataset.
+The names are composed by the actual metric name and the tool that was used to calculate them.
+For instance, \textit{McCabe\_clmt} denotes that the metric name is the McCabe cyclomatic complexity generated by the \textit{clmt} tool, while \textit{McCabe\_ckjm} means that it is the same metric calculated by the \textit{ckjm} tool.
+
+Filenames, methods, classes and package names along with other identifiers are stored in the \textit{identifiers} table.
+Note that each measurement has a related filename and a related identifier that points to a software element.
+For example the \textit{afferent coupling} metric for the module in the directory ``com/scalagent/jmx'' is related to the identifier \textit{com.scalagent.jmx}.
+Finally, the database table \textit{project} contains the related project identifiers, directly extracted from the maven repository.
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.65]{database-schema}
+\caption{The database schema.}
+\label{fig:database-schema}
+\end{figure*}
+
+\section{Research Opportunities}
+\label{sec:research-opportunities}
+
+The measurements provided by our dataset, can be used by researchers and practitioners alike.
+Researchers can use the data to experiment with new software quality models, or validate them with real projects.
+Practitioners who develop tools that calculate metrics can use the dataset to validate if their tools produce correct results.
+
+The dataset also includes the {\sc dsl}-related metrics, which quantifies the usage of basic {\sc dsl} application libraries that are already shipped with the Java {\sc sdk}.
+These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section.
+
+Finally, our dataset can be used side-by-side with the ones presented by Mitropoulos et al.~\cite{HP04} and Raemaekers et al.~\cite{RDV13} in order to examine the datasets for metric correlations.
+This is because their datasets were also produced by analyzing projects coming from the Maven repository.
+
+\section{Experimenting with the Dataset}
+\label{sec:dsl}
+
+\begin{table}
+\centering
+\caption{Top {\sc dsl} Usage Combinations.}
+\label{tbl:dsl-top-usage}
+\begin{tabular}{l r}
+ \hline
+\textbf{DSLs} & \textbf{Count}\\
+\hline
+XML & 1,561\\
+Regex & 909\\
+SQL & 493\\
+XML, XSLT & 475\\
+Regex, XML, XSLT & 158\\
+Regex, XML & 303\\
+SQL, XML & 162\\
+Regex, SQL & 116\\
+Regex, SQL, XML, XSLT & 80\\
+Regex, SQL, XML & 71\\
+SQL, XML, XSLT & 54\\
+XML, XPath & 50\\
+\hline
+\end{tabular}
+\end{table}
+
+The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of {\sc dsl}s in multiple Java projects.
+The related metrics can be found in the database table named \textit{measuremnt\_type}, and they are the following: \textit{RTFUsage}, \textit{RegexUsage}, \textit{HTMLUsage}, \textit{HTMLUsage}, \textit{XPathUsage}, \textit{XSLTUsage}, \textit{XMLUsage}, \textit{SQLUsage}, and \textit{DSLCount}.
+A Python script that analysed the measurements stored in the database, we produced the results illustrated in Table~\ref{tbl:dsl-top-usage}.
+This table, lists popular {\sc dsl} usage combinations found in our dataset.
+An interesting observation is that {\sc xml} is the most widespread {\sc dsl} with 1,561 occurrences in 11,365 projects (13\%).
+Regular expressions are also popular with 909 occurrences (7\%).
+Note that the numbers represents the projects where {\sc xml} and regular expressions were used as the only {\sc dsl}.
+
+\section{Limitations}
+\label{sec:limit}
+
+As we mentioned earlier, to produce our dataset we adopted a narrow selection process.
+In particular, we identified and analyzed only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository.
+The latter reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}.
+Since only \textit{clmt} analyses the source code, this resulted in the reduction of the number of measurements that exposed object-oriented and package design issues.
+
+Finally, only one version was analyzed per project (the latest, unless it violated the aforementioned restriction).
+This decision renders the dataset unusable, for research focused on software evolution.
+
+\section{Related Work}
+\label{sec:rel}
+
+The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}.
+Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements.
+
+Also, Mitropoulos et al.
+performed a similar experiment~\cite{MKLGS14}.
+In particular, they used the FindBugs~\cite{HP04} static analysis tool, to analyze a large part of the maven repository.
+Their dataset includes for each {\sc jar}, a corresponding bug collection produced by FindBugs.
+Our work differs from these two approaches since it presents the metrics calculated by the three different static analysis tools that calculate metrics regarding object-oriented design, program size, and package design.
+
+\section{Conclusions}
+\label{sec:conc}
+
+We presented a dataset created by applying three different static analysis tools on Java projects coming from the Maven Central repository.
+The results invlove a variety of software metrics from program size to object-oriented design.
+%In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates made in the repository.
+We have also shown how our data can be used to extract meaningful results concerning {\sc dsl} usage in Java Projects.
+
+As we discussed, our selection process was strict, filtering out projects that did not have the project's sources.
+However, we are planning to expand our project coverage in the future and include projects that cannot be analysed by all tools (due to source code unavailability).
+Finally, by including all versions for each project we can allow researchers to use our dataset in the evolution context.
+
+\section{Availability}
+
+The dataset and the source code of this publication, along with some utility scripts are available at \url{https://github.com/bkarak/data_msr2015}.
+The {\sc sql} dump of the database is available at \url{http://gaijin.dmst.aueb.gr/~bkarak/data_msr2015.bz2}.
+
 %
@@
 
-\section{Conclusion}
-The conclusion goes here.
-
-% conference papers do not normally have an appendix
-
 % use section* for acknowledgement
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
+\bibliographystyle{IEEEtran}
+\bibliography{msr}
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
-
-% that's all folks
 \end{document}

### 2015-03-29 msr2015-camera-ready.tex
updated msr2015-camera-ready

@@
-%% This style is provided for the ICSE 2015 main conference,
-%% ICSE 2015 co-located events, and ICSE 2015 workshops.
-
-%% bare_conf_ICSE15.tex
-%% V1.4
-%% 2014/05/22
-
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE!
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
 \documentclass[conference]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
 
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-%\author{\IEEEauthorblockN{Michael Shell}
-%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-%Georgia Institute of Technology\\
-%Atlanta, Georgia 30332--0250\\
-%Email: http://www.michaelshell.org/contact.html}
-%\and
-%\IEEEauthorblockN{Homer Simpson}
-%\IEEEauthorblockA{Twentieth Century Fox\\
-%Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\and
-%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-%\IEEEauthorblockA{Starfleet Academy\\
-%San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212\\
-%Fax: (888) 555--1212}}
+\author{\IEEEauthorblockN{Vassilios Karakoidas\IEEEauthorrefmark{1},
+Dimitris Mitropoulos\IEEEauthorrefmark{2},
+Georgios Gousios\IEEEauthorrefmark{3},
+Diomidis Spinellis\IEEEauthorrefmark{1} and
+Panagiotis Louridas\IEEEauthorrefmark{1}}
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
-\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-Homer Simpson\IEEEauthorrefmark{2},
-James Kirk\IEEEauthorrefmark{3},
-Montgomery Scott\IEEEauthorrefmark{3} and
-Eldon Tyrell\IEEEauthorrefmark{4}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-Georgia Institute of Technology,
-Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-Email: homer@thesimpsons.com}
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-Telephone: (800) 555--1212, Fax: (888) 555--1212}
-\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}}
+\IEEEauthorblockA{\IEEEauthorrefmark{3}}
+}
 
@@
 % no keywords
+Java, Software Metrics, Chidamber and Kemerer, Maven
 
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+%\IEEEpeerreviewmaketitle
 
@@
 
-\begin{table}
+\begin{table}[!t]
 \centering
@@
 
+% use section* for acknowledgement
+\section*{Acknowledgment}
+
 %
@@
 
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
-
-% use section* for acknowledgement
-\section*{Acknowledgment}
-
-The authors would like to thank...
-
 % trigger a \newpage just before the given reference

### 2015-03-30 msr2015-camera-ready.tex
updated .gitignore; almost there

@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+%\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 Diomidis Spinellis\IEEEauthorrefmark{1} and
-Panagiotis Louridas\IEEEauthorrefmark{1}}
+Panos Louridas\IEEEauthorrefmark{1}}
 
-\IEEEauthorblockA{\IEEEauthorrefmark{1}}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}}
-\IEEEauthorblockA{\IEEEauthorrefmark{3}}
-}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept of Management Science and Technology\\
+Athens University of Economics and Business\\
+Athens, Greece\\
+\{bkarak,dds,louridas\}@aueb.gr}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Computer Science Department\\
+Columbia University\\
+New York, United States\\
+dimitro@cs.columbia.edu}
+\IEEEauthorblockA{\IEEEauthorrefmark{3}Radboud University Nijmegen\\
+Nijmegen, the Netherlands\\
+g.gousios@cs.ru.nl}}
 
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
@@
 % no keywords
-Java, Software Metrics, Chidamber and Kemerer, Maven
+% Java, Software Metrics, Chidamber and Kemerer, Maven
 
@@
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
 \bibliographystyle{IEEEtran}

### 2015-03-30 msr2015-camera-ready.tex
working on the tables

@@
 \begin{table}[!t]
-\centering
 \caption{The selected Maven projects' size metrics.}
 \label{tbl:oss-size-metrics}
-\begin{tabular}{l r}
+\centering
+\begin{tabular}{|l||r|}
  \hline
@@
 Project Count & 11,365\\
+\hline
 File Count & 449,213\\
+\hline
 Package Count & 59,436\\
+\hline
 Lines of Code & 74,565,772\\
+\hline
 Source Lines of Code & 40,921,287\\
+\hline
 Comment Lines of Code & 25,268,959\\
+\hline
 Number of Classes & 370,518\\
+\hline
 Number of Interfaces & 66,352\\
+\hline
 Number of Enumerations & 9,879\\
+\hline
 Measurement Count & 32,844,836\\
@@
 \label{tbl:dsl-list}
-\begin{tabular}{l l}
+\begin{tabular}{|l||l|}
  \hline
@@
 Regular Expressions & \verb|java.util.regex|\\
+\hline
 XML & \verb|javax.xml|, \verb|org.w3c| and \verb|org.xml|\\
+\hline
 SQL & \verb|java.sql| and \verb|javax.sql|\\
+\hline
 XPath & \verb|java.xml.xpath|\\
+\hline
 XSLT & \verb|javax.xml.transform|\\
+\hline
 RTF & \verb|javax.swing.text.rtf|\\
+\hline
 HTML & \verb|javax.swing.text.html|\\
@@
 \begin{table}[!t]
-\centering
 \caption{Class Design Metrics.}
 \label{tbl:class-selected-metrics}
-\begin{tabular}{l l}
+\centering
+\begin{tabular}{|l||l|}
 \hline
 Depth Of Inheritance Tree & \textit{ckjm}\\
+\hline
 Coupling Between Objects & \textit{ckjm}\\
+\hline
 Weighted Methods Per Class & \textit{ckjm}\\
+\hline
 Response For Class & \textit{ckjm}\\
+\hline
 Lack Of Cohesion In Methods & \textit{ckjm}\\
+\hline
 Number Of Children & \textit{ckjm}\\
+\hline
 Attribute Hiding Factor & \textit{clmt}\\
+\hline
 Coupling Between Methods & \textit{ckjm}\\
+\hline
 Average Method Complexity & \textit{ckjm}\\
+\hline
 Cohesion Among Methods of Class & \textit{ckjm}\\
+\hline
 Data Access Metric & \textit{ckjm, clmt}\\
+\hline
 Inheritance Coupling & \textit{ckjm}\\
+\hline
 Lack Of Cohesion In Methods3 & \textit{ckjm}\\
+\hline
 Measure Of Aggregation & \textit{ckjm}\\
+\hline
 Measure Of Functional Abstraction & \textit{ckjm}\\
+\hline
 Number of Attributes & \textit{clmt}\\
+\hline
 Method Hiding Factor & \textit{clmt}\\
@@
 \begin{table}[!t]
-\centering
 \caption{Method Design Metrics.}
 \label{tbl:method-selected-metrics}
-\begin{tabular}{l l}
+\centering
+\begin{tabular}{|l||l|}
 \hline
 Number of Method Parameters & \textit{clmt}\\
+\hline
 Number of Methods & \textit{clmt, ckjm}\\
+\hline
 McCabe Cyclomatic Complexity & \textit{ckjm, clmt}\\
@@
 \begin{table}[!t]
-\centering
 \caption{Package Design Metrics.}
 \label{tbl:package-selected-metrics}
-\begin{tabular}{l l}
+\centering
+\begin{tabular}{|l||l|}
 \hline
 Number of Concrete Classes & \textit{jdep}\\
+\hline
 Afferent Couplings & \textit{jdep, ckjm}\\
+\hline
 Efferent Couplings & \textit{jdep, ckjm}\\
+\hline
 Instability & \textit{jdep}\\
+\hline
 Abstractness & \textit{jdep}\\
+\hline
 Distance Main Sequence & \textit{jdep}\\
@@
 \begin{table}[!t]
-\centering
 \caption{Program Size Metrics.}
 \label{tbl:size-selected-metrics}
-\begin{tabular}{l l}
+\centering
+\begin{tabular}{|l||l|}
  \hline
 Number of Classes & \textit{clmt, ckjm, jdep}\\
+\hline
 Number of Enumerations & \textit{clmt, ckjm}\\
+\hline
 Number of Interfaces & \textit{clmt, ckjm}\\
+\hline
 Module Count & \textit{clmt, ckjm}\\
+\hline
 Comments Lines Of Code & \textit{clmt}\\
+\hline
 Lines Of Code & \textit{clmt, ckjm}\\
+\hline
 Source Lines Of Code & \textit{clmt}\\
+\hline
 Function Oriented Code & \textit{clmt}\\
+\hline
 DSL Usage Count & \textit{clmt}\\
+\hline
 RTF Usage Count & \textit{clmt}\\
+\hline
 Regex Usage Count & \textit{clmt}\\
+\hline
 HTML Usage Count & \textit{clmt}\\
+\hline
 XPath Usage Count & \textit{clmt}\\
+\hline
 XSLT Usage Count & \textit{clmt}\\
+\hline
 XML Usage Count & \textit{clmt}\\
+\hline
 SQL Usage Count & \textit{clmt}\\
+\hline
 File Count & \textit{clmt}\\

### 2015-03-30 msr2015-camera-ready.tex
added ACK

@@
 \begin{table}[!t]
-\centering
 \caption{Top {\sc dsl} Usage Combinations.}
 \label{tbl:dsl-top-usage}
-\begin{tabular}{l r}
+\centering
+\begin{tabular}{|l||r|}
  \hline
@@
 XML & 1,561\\
+\hline
 Regex & 909\\
+\hline
 SQL & 493\\
+\hline
 XML, XSLT & 475\\
+\hline
 Regex, XML, XSLT & 158\\
+\hline
 Regex, XML & 303\\
+\hline
 SQL, XML & 162\\
+\hline
 Regex, SQL & 116\\
+\hline
 Regex, SQL, XML, XSLT & 80\\
+\hline
 Regex, SQL, XML & 71\\
+\hline
 SQL, XML, XSLT & 54\\
+\hline
 XML, XPath & 50\\
@@
 
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
+This research has been co-financed by the European Union (European So- cial Fund esf) and Greek national funds through the Operational Program ``Education and Lifelong Learning'' of the National Strategic Reference Frame- work (nsrf) - Research Funding Program: Thalis Athens University of Economics and Business - software engineering research platform.
 

### 2015-03-30 msr2015-camera-ready.tex
final touch

@@
 %\hyphenation{op-tical net-works semi-conduc-tor}
+
+\clubpenalty = 10000
+\widowpenalty = 10000
+\displaywidowpenalty = 10000
+
+\usepackage{flushend}
 
@@
 
-This research has been co-financed by the European Union (European So- cial Fund esf) and Greek national funds through the Operational Program ``Education and Lifelong Learning'' of the National Strategic Reference Frame- work (nsrf) - Research Funding Program: Thalis Athens University of Economics and Business - software engineering research platform.
+This research has been co-financed by the European Union (European Social Fund esf) and Greek national funds through the Operational Program ``Education and Lifelong Learning'' of the National Strategic Reference Framework (nsrf) - Research Funding Program: Thalis Athens University of Economics and Business - software engineering research platform.
 

### 2015-03-30 msr2015-camera-ready.tex
paper ready for submission

@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
+
 \title{Generating the Blueprints of the Java Ecosystem}
@@
 Dimitris Mitropoulos\IEEEauthorrefmark{2},
-Georgios Gousios\IEEEauthorrefmark{3},
-Diomidis Spinellis\IEEEauthorrefmark{1} and
-Panos Louridas\IEEEauthorrefmark{1}}
+Panos Louridas\IEEEauthorrefmark{1},
+Georgios Gousios\IEEEauthorrefmark{3} and
+Diomidis Spinellis\IEEEauthorrefmark{1}}
 
@@
 
-The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology presented in reference \cite{MKLGS14}.
+The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. In general, it follows the same methodology as Mitropoulos et al. \cite{MKLGS14}.
 
@@
 The process to identify them was the following; Every project consists of two {\sc jar} files, one that contains a compiled version of the project and one that contains the source code.
-The projects that did not had both binary and source {\sc jar}s, were excluded from the experiment.
+The projects that did not have both binary and source {\sc jar}s, were excluded from the experiment.
 When the source {\sc jar} file was downloaded, it was scanned for Java source files.
@@
 These kind of metrics, can be really useful for researchers that focus on {\sc dsl} embedding, or study {\sc dsl} usage patterns~\cite{KARA14} as we illustrate in the following section.
+In addition, the dataset covers a significant portion of the Maven repository, it can be used for large scale empirical studies.
 
@@
 In particular, we identified and analyzed only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository.
-The latter reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}.
+The former reduced significantly the number of projects that were analyzed, because many of them provided only the binary {\sc jar}.
 Since only \textit{clmt} analyses the source code, this resulted in the reduction of the number of measurements that exposed object-oriented and package design issues.
@@
 We presented a dataset created by applying three different static analysis tools on Java projects coming from the Maven Central repository.
-The results invlove a variety of software metrics from program size to object-oriented design.
-%In the future, we plan to keep an updated version of the dataset, by analysing the new additions and updates made in the repository.
+The results involve a variety of software metrics from program size to object-oriented design.
 We have also shown how our data can be used to extract meaningful results concerning {\sc dsl} usage in Java Projects.
